### 2024-06-07 paper/paper.tex
Basic paper setup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
% History:
%
% - TEMPLATE for Usenix papers, specifically to meet requirements of
%   USENIX '05. originally a template for producing IEEE-format
%   articles using LaTeX. written by Matthew Ward, CS Department,
%   Worcester Polytechnic Institute. adapted by David Beazley for his
%   excellent SWIG paper in Proceedings, Tcl 96. turned into a
%   smartass generic template by De Clarke, with thanks to both the
%   above pioneers. Use at your own risk. Complaints to /dev/null.
%   Make it two column with no page numbering, default is 10 point.
%
% - Munged by Fred Douglis <douglis@research.att.com> 10/97 to
%   separate the .sty file from the LaTeX source template, so that
%   people can more easily include the .sty file into an existing
%   document. Also changed to more closely follow the style guidelines
%   as represented by the Word sample file.
%
% - Note that since 2010, USENIX does not require endnotes. If you
%   want foot of page notes, don't include the endnotes package in the
%   usepackage command, below.
% - This version uses the latex2e styles, not the very ancient 2.09
%   stuff.
%
% - Updated July 2018: Text block size changed from 6.5" to 7"
%
% - Updated Dec 2018 for ATC'19:
%
%   * Revised text to pass HotCRP's auto-formatting check, with
%     hotcrp.settings.submission_form.body_font_size=10pt, and
%     hotcrp.settings.submission_form.line_height=12pt
%
%   * Switched from \endnote-s to \footnote-s to match Usenix's policy.
%
%   * \section* => \begin{abstract} ... \end{abstract}
%
%   * Make template self-contained in terms of bibtex entires, to allow
%     this file to be compiled. (And changing refs style to 'plain'.)
%
%   * Make template self-contained in terms of figures, to
%     allow this file to be compiled. 
%
%   * Added packages for hyperref, embedding fonts, and improving
%     appearance.
%   
%   * Removed outdated text.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{style}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

% inlined bib file
\usepackage{filecontents}

%-------------------------------------------------------------------------------
\begin{filecontents}{\jobname.bib}
%-------------------------------------------------------------------------------
@Book{arpachiDusseau18:osbook,
author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
title =        {Operating Systems: Three Easy Pieces},
publisher =    {Arpaci-Dusseau Books, LLC},
year =         2015,
edition =      {1.00},
note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
}
@InProceedings{waldspurger02,
author =       {Waldspurger, Carl A.},
title =        {Memory resource management in {VMware ESX} server},
booktitle =    {USENIX Symposium on Operating System Design and
Implementation (OSDI)},
year =         2002,
pages =        {181--194},
note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
\end{filecontents}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Redstone: a Deterministic Simulation Testing Framework for Distributed Systems}

%for single author (just remove % characters)
\author{
{\rm Benjamin Friedman}\\
% Your Institution
\and
{\rm Katherine Li}\\
% Second Institution
\and
{\rm Matthew Mattei}\\
\and
{\rm Ron Dubinsky}\\
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Your abstract text goes here. Just a few facts. Whet our appetites.
Not more than 200 words, if possible, and preferably closer to 150.
\end{abstract}

%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------

A paragraph of text goes here. Lots of text. Plenty of interesting
text. Text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text text text text text text text text
text text text text text text text.
More fascinating text. Features galore, plethora of promises.

%-------------------------------------------------------------------------------
\section{Footnotes, Verbatim, and Citations}
%-------------------------------------------------------------------------------

Footnotes should be places after punctuation characters, without any
spaces between said characters and footnotes, like so.%
\footnote{Remember that USENIX format stopped using endnotes and is
now using regular footnotes.} And some embedded literal code may
look as follows.

\begin{verbatim}
int main(int argc, char *argv[]) 
{
return 0;
}
\end{verbatim}

Now we're going to cite somebody. Watch for the cite tag. Here it
comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
about resource management in the ESX hypervisor~\cite{waldspurger02}.

The tilde character (\~{}) in the tex source means a non-breaking
space. This way, your reference will always be attached to the word
that preceded it, instead of going to the next line.

And the 'cite' package sorts your citations by their numerical order
of the corresponding references at the end of the paper, ridding you
from the need to notice that, e.g, ``Waldspurger'' appears after
``Arpachi-Dusseau'' when sorting references
alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.

It'd be nice and thoughtful of you to include a suitable link in each
and every bibtex entry that you use in your submission, to allow
reviewers (and other readers) to easily get to the cited work, as is
done in all entries found in the References section of this document.

Now we're going take a look at Section~\ref{sec:figs}, but not before
observing that refs to sections and citations and such are colored and
clickable in the PDF because of the packages we've included.

%-------------------------------------------------------------------------------
\section{Floating Figures and Lists}
\label{sec:figs}
%-------------------------------------------------------------------------------

%---------------------------
\begin{figure}
\begin{center}
\begin{tikzpicture}
\draw[thin,gray!40] (-2,-2) grid (2,2);
\draw[<->] (-2,0)--(2,0) node[right]{$x$};
\draw[<->] (0,-2)--(0,2) node[above]{$y$};
\draw[line width=2pt,blue,-stealth](0,0)--(1,1)
node[anchor=south west]{$\boldsymbol{u}$};
\draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
node[anchor=north east]{$\boldsymbol{-u}$};
\end{tikzpicture}
\end{center}
\caption{\label{fig:vectors} Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. Text size inside figure should be as big as
caption's text. }
\end{figure}
%% %---------------------------

Here's a typical reference to a floating figure:
Figure~\ref{fig:vectors}. Floats should usually be placed where latex
wants then. Figure\ref{fig:vectors} is centered, and has a caption
that instructs you to make sure that the size of the text within the
figures that you use is as big as (or bigger than) the size of the
text in the caption of the figures. Please do. Really.

In our case, we've explicitly drawn the figure inlined in latex, to
allow this tex file to cleanly compile. But usually, your figures will
reside in some file.pdf, and you'd include them in your document
with, say, \textbackslash{}includegraphics.

Lists are sometimes quite handy. If you want to itemize things, feel
free:

\begin{description}

\item[fread] a function that reads from a \texttt{stream} into the
array \texttt{ptr} at most \texttt{nobj} objects of size
\texttt{size}, returning returns the number of objects read.

\item[Fred] a person's name, e.g., there once was a dude named Fred
who separated usenix.sty from this file to allow for easy
inclusion.
\end{description}

\noindent
The noindent at the start of this paragraph in its tex version makes
it clear that it's a continuation of the preceding paragraph, as
opposed to a new paragraph in its own right.

\subsection{LaTeX-ing Your TeX File}
%-----------------------------------

People often use \texttt{pdflatex} these days for creating pdf-s from
tex files via the shell. And \texttt{bibtex}, of course. Works for us.

%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

The USENIX latex style is old and very tired, which is why
there's no \textbackslash{}acks command for you to use when
acknowledging. Sorry.

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

USENIX program committees give extra points to submissions that are
backed by artifacts that are publicly available. If you made your code
or data available, it's worth mentioning this fact in a dedicated
section.

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{\jobname}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks

### 2024-06-07 paper/paper.tex
Abstract done

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Redstone: a Deterministic Simulation Testing Framework for Distributed Systems}
+\title{\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}
 
@@
 %-------------------------------------------------------------------------------
-Your abstract text goes here. Just a few facts. Whet our appetites.
-Not more than 200 words, if possible, and preferably closer to 150.
+In testing distributed systems,
+confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
+Redstone, a modular deterministic simulation testing framework,
+amplifies failures in various substrates underlying a distributed system
+in order to confirm the system's ability to withstand these failures.
+We intercept calls to the kernel for the disk and the network, as well as to clock functions,
+introducing our own code.
+Determinism allows reproduction of failure conditions,
+allowing developers to confirm, having encountered and debugged a failure,
+that their system will not fail again when confronted by identical conditions.
+Our control over clock functions further allows us to "accelerate" time,
+increasing ability to test faster, and to emulate the effects of clock jitter.
+Finally, because Redstone is inherently modular,
+it is simple to extend and port to a wider variety of applications and platforms.
 \end{abstract}
@@
 
-%-------------------------------------------------------------------------------
-\section{Footnotes, Verbatim, and Citations}
-%-------------------------------------------------------------------------------
+% %-------------------------------------------------------------------------------
+% \section{Footnotes, Verbatim, and Citations}
+% %-------------------------------------------------------------------------------
+% 
+% Footnotes should be places after punctuation characters, without any
+% spaces between said characters and footnotes, like so.%
+% \footnote{Remember that USENIX format stopped using endnotes and is
+% now using regular footnotes.} And some embedded literal code may
+% look as follows.
+% 
+% \begin{verbatim}
+% int main(int argc, char *argv[]) 
+% {
+% return 0;
+% }
+% \end{verbatim}
+% 
+% Now we're going to cite somebody. Watch for the cite tag. Here it
+% comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
+% book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
+% Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
+% about resource management in the ESX hypervisor~\cite{waldspurger02}.
+% 
+% The tilde character (\~{}) in the tex source means a non-breaking
+% space. This way, your reference will always be attached to the word
+% that preceded it, instead of going to the next line.
+% 
+% And the 'cite' package sorts your citations by their numerical order
+% of the corresponding references at the end of the paper, ridding you
+% from the need to notice that, e.g, ``Waldspurger'' appears after
+% ``Arpachi-Dusseau'' when sorting references
+% alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}. 
+% 
+% It'd be nice and thoughtful of you to include a suitable link in each
+% and every bibtex entry that you use in your submission, to allow
+% reviewers (and other readers) to easily get to the cited work, as is
+% done in all entries found in the References section of this document.
+% 
+% Now we're going take a look at Section~\ref{sec:figs}, but not before
+% observing that refs to sections and citations and such are colored and
+% clickable in the PDF because of the packages we've included.
+% 
+% %-------------------------------------------------------------------------------
+% \section{Floating Figures and Lists}
+% \label{sec:figs}
+% %-------------------------------------------------------------------------------
 
-Footnotes should be places after punctuation characters, without any
-spaces between said characters and footnotes, like so.%
-\footnote{Remember that USENIX format stopped using endnotes and is
-now using regular footnotes.} And some embedded literal code may
-look as follows.
+% %---------------------------
+% \begin{figure}
+% \begin{center}
+% \begin{tikzpicture}
+% \draw[thin,gray!40] (-2,-2) grid (2,2);
+% \draw[<->] (-2,0)--(2,0) node[right]{$x$};
+% \draw[<->] (0,-2)--(0,2) node[above]{$y$};
+% \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
+% node[anchor=south west]{$\boldsymbol{u}$};
+% \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
+% node[anchor=north east]{$\boldsymbol{-u}$};
+% \end{tikzpicture}
+% \end{center}
+% \caption{\label{fig:vectors} Text size inside figure should be as big as
+% caption's text. Text size inside figure should be as big as
+% caption's text. Text size inside figure should be as big as
+% caption's text. Text size inside figure should be as big as
+% caption's text. Text size inside figure should be as big as
+% caption's text. }
+% \end{figure}
+% %% %---------------------------
 
-\begin{verbatim}
-int main(int argc, char *argv[]) 
-{
-return 0;
-}
-\end{verbatim}
-
-Now we're going to cite somebody. Watch for the cite tag. Here it
-comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
-book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
-Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
-about resource management in the ESX hypervisor~\cite{waldspurger02}.
-
-The tilde character (\~{}) in the tex source means a non-breaking
-space. This way, your reference will always be attached to the word
-that preceded it, instead of going to the next line.
-
-And the 'cite' package sorts your citations by their numerical order
-of the corresponding references at the end of the paper, ridding you
-from the need to notice that, e.g, ``Waldspurger'' appears after
-``Arpachi-Dusseau'' when sorting references
-alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}.
-
-It'd be nice and thoughtful of you to include a suitable link in each
-and every bibtex entry that you use in your submission, to allow
-reviewers (and other readers) to easily get to the cited work, as is
-done in all entries found in the References section of this document.
-
-Now we're going take a look at Section~\ref{sec:figs}, but not before
-observing that refs to sections and citations and such are colored and
-clickable in the PDF because of the packages we've included.
-
-%-------------------------------------------------------------------------------
-\section{Floating Figures and Lists}
-\label{sec:figs}
-%-------------------------------------------------------------------------------
-
-%---------------------------
-\begin{figure}
-\begin{center}
-\begin{tikzpicture}
-\draw[thin,gray!40] (-2,-2) grid (2,2);
-\draw[<->] (-2,0)--(2,0) node[right]{$x$};
-\draw[<->] (0,-2)--(0,2) node[above]{$y$};
-\draw[line width=2pt,blue,-stealth](0,0)--(1,1)
-node[anchor=south west]{$\boldsymbol{u}$};
-\draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
-node[anchor=north east]{$\boldsymbol{-u}$};
-\end{tikzpicture}
-\end{center}
-\caption{\label{fig:vectors} Text size inside figure should be as big as
-caption's text. Text size inside figure should be as big as
-caption's text. Text size inside figure should be as big as
-caption's text. Text size inside figure should be as big as
-caption's text. Text size inside figure should be as big as
-caption's text. }
-\end{figure}
-%% %---------------------------
-
-Here's a typical reference to a floating figure:
-Figure~\ref{fig:vectors}. Floats should usually be placed where latex
-wants then. Figure\ref{fig:vectors} is centered, and has a caption
-that instructs you to make sure that the size of the text within the
-figures that you use is as big as (or bigger than) the size of the
-text in the caption of the figures. Please do. Really.
-
-In our case, we've explicitly drawn the figure inlined in latex, to
-allow this tex file to cleanly compile. But usually, your figures will
-reside in some file.pdf, and you'd include them in your document
-with, say, \textbackslash{}includegraphics.
-
-Lists are sometimes quite handy. If you want to itemize things, feel
-free:
-
-\begin{description}
-
-\item[fread] a function that reads from a \texttt{stream} into the
-array \texttt{ptr} at most \texttt{nobj} objects of size
-\texttt{size}, returning returns the number of objects read.
-
-\item[Fred] a person's name, e.g., there once was a dude named Fred
-who separated usenix.sty from this file to allow for easy
-inclusion.
-\end{description}
-
-\noindent
-The noindent at the start of this paragraph in its tex version makes
-it clear that it's a continuation of the preceding paragraph, as
-opposed to a new paragraph in its own right.
-
-\subsection{LaTeX-ing Your TeX File}
-%-----------------------------------
-
-People often use \texttt{pdflatex} these days for creating pdf-s from
-tex files via the shell. And \texttt{bibtex}, of course. Works for us.
+% Here's a typical reference to a floating figure:
+% Figure~\ref{fig:vectors}. Floats should usually be placed where latex
+% wants then. Figure\ref{fig:vectors} is centered, and has a caption
+% that instructs you to make sure that the size of the text within the
+% figures that you use is as big as (or bigger than) the size of the
+% text in the caption of the figures. Please do. Really.
+% 
+% In our case, we've explicitly drawn the figure inlined in latex, to
+% allow this tex file to cleanly compile. But usually, your figures will
+% reside in some file.pdf, and you'd include them in your document
+% with, say, \textbackslash{}includegraphics.
+% 
+% Lists are sometimes quite handy. If you want to itemize things, feel
+% free:
+% 
+% \begin{description}
+% 
+% \item[fread] a function that reads from a \texttt{stream} into the
+% array \texttt{ptr} at most \texttt{nobj} objects of size
+% \texttt{size}, returning returns the number of objects read.
+% 
+% \item[Fred] a person's name, e.g., there once was a dude named Fred
+% who separated usenix.sty from this file to allow for easy
+% inclusion.
+% \end{description}
+% 
+% \noindent
+% The noindent at the start of this paragraph in its tex version makes
+% it clear that it's a continuation of the preceding paragraph, as
+% opposed to a new paragraph in its own right.
+% 
+% 
+% \subsection{LaTeX-ing Your TeX File}
+% %-----------------------------------
+% 
+% People often use \texttt{pdflatex} these days for creating pdf-s from
+% tex files via the shell. And \texttt{bibtex}, of course. Works for us.
 

### 2024-06-07 paper/paper.tex
Paper work

@@
 
-\documentclass[letterpaper,twocolumn,10pt]{article}
+\documentclass[letterpaper,twocolumn]{article}
+
 \usepackage{style}
@@
 \usepackage{filecontents}
+
+\usepackage{setspace}
+\linespread{1.25}
 
@@
 %-------------------------------------------------------------------------------
+{\fontsize{12}{15}\selectfont 
 In testing distributed systems,
@@
 it is simple to extend and port to a wider variety of applications and platforms.
+}
 \end{abstract}
@@
 
-A paragraph of text goes here. Lots of text. Plenty of interesting
-text. Text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text text text text text text text text
-text text text text text text text.
-More fascinating text. Features galore, plethora of promises.
+{\fontsize{12}{15}\selectfont 
+Distributed systems are complicated ones,
+because they rely not only on the particular machines
+on which the systems run but also on the network connecting these machines.
+As such, distributed systems must contain many
+(often complicated and difficult-to-reason-about)
+mechanisms by which to recover from both network and machine failures
+(more specifically, network latency, disk I/O failure, bugs in the kernel,
+and all manners of timing-based bugs).
+
+Testing offers the ability to confirm that a system can withstand failures.
+Specifically, if one can introduce a failure and check that the system withstands it,
+it certainly increases the degree of trust in the system.
+However, in order to be effective,
+such testing must be able to consistently introduce failures.
+Just hoping that failures naturally occur in the process of testing is a non-starter;
+they must be introduced.
+In order to introduce failures, the system must have control of the network, disk,
+and time systems on which a distributed system relies.
+Therefore, the system must simulate this functionality whilst also injecting failure where possible.
+
+"Consistently" is another key phrase here,
+as a test must be replicable.
+% just running the system a few times doesn't confirm that everything that can go wrong has gone wrong.
+As such,
+a good testing system must not only introduce failures,
+but be able to repeatedly introduce exactly the same failures in exactly the same way.
+In the words of John Ousterhout,
+"the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
+Therefore, our system must be \textit{deterministic}.
+
+Furthermore,
+distributed systems often run on comparatively long time-scales:
+a system may be running for months or years,
+hopefully without failure.
+However,
+it is unrealistic to spend months testing a system to confirm that such durations will not lead to failure.
+But, with control of the machine's time system calls,
+we can effectively "accelerate" time in the test,
+meaning the distributed system to be tested will act as though it has been running for such a duration,
+without interrupting development for such an extended period of time.
+
+Finally,
+distributed systems are highly varied,
+and as a result may require features or platform support not foreseen by our implementation.
+Modularity in our design allows our framework to be easily extended,
+not future-proofing it but allowing it to be future-proofed.
+}
+
+\section{Related Work}
+
+{\fontsize{12}{15}\selectfont 
+Though not a research paper,
+Redstone was inspired by work done by the TigerBeetle team,
+and their work in testing the TigerBeetle database.
+This work heavily involves hastened testing of simulated distributed system faults.
+However, the limitation of their work is that their simulator is compiled specifically for their software.
+While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
+there are many, many more distributed systems in the real world that are a poor match for this form of simulation.
+As such, we wanted to try to take the idea they built their replicator on.
+The basis of their simulator involves mocking all input and output:
+their work includes a network simulator to force network faults and latencies,
+and an in-memory storage simulator to force storage faults and latencies.
+The simulator then speeds up the clock to make these I/O operations occur far more frequently than in production,
+causing faults that may only occur once a year, or even more infrequently, to occur in a matter of days.
+Such functionality would be highly valuable in testing nearly any production distributed system,
+but, again, the context of TigerBeetle’s work is highly specific.
+As such, we wanted to develop a framework that incorporates a number of the basic simulations TigerBeetle’s simulator includes
+(namely, hastened I/O faults for network and in-memory storage),
+but one that can be generally implemented on normal systems and run a much broader range of applications.
+}
+
+% Distributed systems are fucking stupid.
+% 
+% Therefore, in order to combat this stupidity, there was the advent of a concept of "testing".
+% This dark and arcane art is wonderfully usable but falls flat when tested conditions occur only
+% rarely. The best example of such wild conditions are things like network latencies, disk
+% io errors, kernel bugs, time, and more. Everything has some level of doing a fucky wucky,
+% so our job is to make these fucky wuckies happen more often so that programmers are better able to
+% understand how their system handles such fucky wuckies
+% A paragraph of text goes here. Lots of text. Plenty of interesting
+% text. Text text text text text text text text text text text text text
+% text text text text text text text text text text text text text text
+% text text text text text text text text text text text text text text
+% text text text text text text text.
+% More fascinating text. Features galore, plethora of promises.
 

### 2024-06-07 paper/paper.tex
Shakespearized first two sections

@@
 that their system will not fail again when confronted by identical conditions.
-Our control over clock functions further allows us to "accelerate" time,
+Our control over clock functions further allows us to ``accelerate" time,
 increasing ability to test faster, and to emulate the effects of clock jitter.
@@
 it is simple to extend and port to a wider variety of applications and platforms.
+
 }
@@
 
-"Consistently" is another key phrase here,
+``Consistently" is another key phrase here,
 as a test must be replicable.
@@
 In the words of John Ousterhout,
-"the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
+``the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
 Therefore, our system must be \textit{deterministic}.
@@
 not future-proofing it but allowing it to be future-proofed.
+
 }
@@
 \section{Related Work}
+% Redstone was inspired by work done by the TigerBeetle team,
+% and their work in testing the TigerBeetle database.
+% However, the limitation of their work is that their simulator is compiled specifically for their software.
 
 {\fontsize{12}{15}\selectfont 
-Though not a research paper,
-Redstone was inspired by work done by the TigerBeetle team,
-and their work in testing the TigerBeetle database.
-This work heavily involves hastened testing of simulated distributed system faults.
-However, the limitation of their work is that their simulator is compiled specifically for their software.
+Although their work is not a research paper,
+the TigerBeetle team has provided inspiration to Redstone in their work developing a testing system for their database.
+This work heavily involved hastened testing of simulated distributed system faults.
+However, a significant limiting factor in their work as compared to ours is that the simulator is compiled specifically for the software being tested.
 While this setup works for their well-abstracted code that they can freely recompile to embed the simulation,
-there are many, many more distributed systems in the real world that are a poor match for this form of simulation.
-As such, we wanted to try to take the idea they built their replicator on.
+there are many, many more distributed systems in the real world that this form of simulation suits poorly at best.
+
+As such, we wanted to try to emulate the idea on which they built their replicator.
 The basis of their simulator involves mocking all input and output:
@@
 and an in-memory storage simulator to force storage faults and latencies.
-The simulator then speeds up the clock to make these I/O operations occur far more frequently than in production,
+The simulator then speeds up the clock to make I/O operations occur far more frequently than in production,
 causing faults that may only occur once a year, or even more infrequently, to occur in a matter of days.
-Such functionality would be highly valuable in testing nearly any production distributed system,
-but, again, the context of TigerBeetle’s work is highly specific.
-As such, we wanted to develop a framework that incorporates a number of the basic simulations TigerBeetle’s simulator includes
-(namely, hastened I/O faults for network and in-memory storage),
+Such functionality would be highly valuable in testing nearly any production distributed system.
+
+Therefore,
+we wanted to develop a framework that incorporates a number of features from the basic simulation methodologies
+TigerBeetle’s simulator includes (namely, hastened I/O faults for network and in-memory storage),
 but one that can be generally implemented on normal systems and run a much broader range of applications.
+
 }

### 2024-06-07 paper/paper.tex
Writeup continued

@@
 
+\section{System Call Interception}
+
+{\fontsize{12}{15}\selectfont 
+In order for Redstone to perform its role of replacing the implementation of system calls,
+we need some method of intercepting calls made to the system library and,
+conditional on whether we seek to alter their behavior,
+replacing them.
+
+Initially, we planned to use \texttt{LD\_PRELOAD},
+a feature of the dynamic linker,
+which allows a user-created shared library to override weakly linked \texttt{libc} symbols on process start.
+Unfortunately,
+\texttt{LD\_PRELOAD} is often finicky and can be unreliable,
+as we saw in our own attempts to use it,
+causing us to opt not to employ it and to instead seek alternatives.
+One option was to simply link in a static library containing all the overridden functions.
+This would have meant that the targeted program would need to be compilable specifically for use with Redstone.
+This was decided to be a barrier to the goal of easy simulation without code changes to the program to be tested,
+so we opted for the second fallback: the \texttt{ptrace(2)} system call.
+
+\texttt{ptrace(2)} is used by debuggers to fully control a child process,
+which gives the user a lot of power over the simulated processes.
+Unfortunately,
+with great power came a significant amount of overhead.
+Using the \texttt{PTRACE\_SYSCALL} request,
+Redstone runs the program until a syscall instruction is issued,
+at which point it accepts the arguments,
+the syscall number, and some other state.
+We pass this information, as well as the syscall identifier,
+to a platform-agnostic hooks table that, if possible,  calls the relevant hook.
+If no hook is present for the given syscall,
+Redstone passes the syscall through to the kernel and continue the program's execution.
+If a hook is present for the given syscall,
+and returns that it has successfully handled the given request,
+Redstone first replaces the syscall number with that of \texttt{getpid}
+(a cheap syscall that doesn’t take any arguments and has no side effects),
+then changes the program registers to replace the syscall return value with our result.
+For obvious reasons, this is quite slow.
+The \texttt{PTRACE\_SYSEMU} command
+(which just doesn’t execute the system call, allowing us to set the return value instead)
+can reduce this overhead,
+but not by any meaningful amount.
+We have more data on the specific overheads imposed by the \texttt{ptrace} runner in the evaluation section.
+
+Aside from the overheads imposed by \texttt{ptrace},
+there is an additional limitation:
+Linux implements some system calls in userspace dynamic libraries for improved performance.
+The modern version of this is known as \texttt{vDSO},
+and unfortunately is not caught by \texttt{PTRACE\_SYSCALL}.
+To counter this, we forcefully disable the use of \texttt{vDSO} on simulated programs upon start,
+falling back to traditional system calls.
+This further worsens the overheads of \texttt{ptrace}.
+
+Owing to the platform-specific nature of interception,
+this part of Redstone is confined to black magic jail,
+and can be easily overridden to boost platform support or improve performance.
+For example,
+if ever \texttt{LD\_PRELOAD} decided to stop being so temperamental,
+effectively only one line of code would need to be changed in order to replace the simulator’s runner with a different implementation.
+
+}
+
 % Distributed systems are fucking stupid.

### 2024-06-07 paper/paper.tex
Beautification
Added architecture section

@@
 %     hotcrp.settings.submission_form.body_font_size=10pt, and
-%     hotcrp.settings.submission_form.line_height=12pt
+%     hotcrp.settings.submission_form.line_height=12.5pt
 %
@@
 
+\newcommand{\vrsdust}[1]{\includegraphics[height=#1]{redstone_dust.png}}
+% \newcommand{\vrswire}[1]{\includegraphics[height=#1]{redstone_wire.png}}
+
+\newcommand{\txtrsdust}{\vrsdust{0.55cm} \hspace{0.1in}}
+% \newcommand{\txtrswire}{\vrswire{0.6cm}
+
 %-------------------------------------------------------------------------------
@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}
+\title{\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}
 
@@
 %-------------------------------------------------------------------------------
-\section{Introduction}
+\section{\txtrsdust Introduction}
 %-------------------------------------------------------------------------------
@@
 
-\section{Related Work}
+\section{\txtrsdust Related Work}
 % Redstone was inspired by work done by the TigerBeetle team,
@@
 
-\section{System Call Interception}
+\section{\txtrsdust Architecture}
+
+\begin{figure}
+\includegraphics[width=0.45\textwidth]{redstone_architecture.jpeg}
+\caption{General architecture of the Redstone framework}
+\end{figure}
+
+{\fontsize{12}{15}\selectfont 
+Figure 1 provides a visual representation of the architecture powering Redstone.
+The region marked "simulator space" represents the simulator process,
+for which system calls are re-routed to the syscall implementations specified for the simulator run.
+Within the simulator process there are multiple “machines”,
+representations of physical machines that, in production, would actually be different machines.
+Each of these machine abstractions have their own simulated disk space.
+Each machine abstraction is associated with a child process,
+called a “replica”,
+of the simulator process that runs the actual functionality expected of the individual machine,
+working with the machine’s “files” (the in-memory storage mocked up by the simulator).
+
+}
+
+\section{\txtrsdust System Call Interception}
 

### 2024-06-07 paper/paper.tex
System call interception coverage

@@
 
+\section{\txtrsdust System Call Interception Coverage}
+
+{\fontsize{12}{15}\selectfont 
+In the process of implementing Redstone,
+we have encountered limitations to the extent and nature of what we can properly intercept and handle.
+These fall into three categories:
+that coverage which may be attained with sufficient work,
+that coverage which is conditionally possible depending on the workload,
+and that which is impossible.
+
+The first category,
+that coverage which may be attained with sufficient work
+contains features like \texttt{epoll}, \texttt{select}, \texttt{poll}, \texttt{io\_uring},
+more exotic network protocols,
+and additional fault classes and more sophisticated fault injection algorithms.
+These can be implemented given sufficient additional time investment.
+
+The second category,
+that coverage which is conditionally possible depending on the workload,
+is more interesting, and perhaps the most common example is that of \texttt{getrandom}.
+Given that Redstone's entire reason for existence is to be as deterministic as possible,
+the naive approach would be to forward to a simulated CPRNG, such as ChaCha20,
+that is seeded by some derivation of the simulation seed.
+Unfortunately, if a program uses randomness for cases like cryptographic key generation,
+and any kind of external accesses occur,
+this indicates the presence of a significant security vulnerability due to reused keys.
+As such,
+randomness remains unimplemented,
+and should only really be implemented assuming we can guarantee that a vulnerability will not occur on a given program.
+
+The third category,
+that which is impossible,
+is introduced by restrictions on userspace.
+\texttt{mmap} is the prime example of this category.
+We have no way of replacing the page-in/page-out handling so this is also left as a passthrough.
+
+}
+
 % Distributed systems are fucking stupid.

### 2024-06-07 paper/paper.tex
Added randomness/determinism section

@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems}
+\title{\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Deterministic Simulation Testing Framework for Distributed Systems}
 
@@
 confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
-Redstone, a modular deterministic simulation testing framework,
+Redstone, a deterministic simulation testing framework,
 amplifies failures in various substrates underlying a distributed system
@@
 We intercept calls to the kernel for the disk and the network, as well as to clock functions,
-introducing our own code.
-Determinism allows reproduction of failure conditions,
+introducing our own code. Our control over clock functions further allows us to ``accelerate" time,
+increasing ability to test faster, and to emulate the effects of clock jitter.
+Additionally, our framework has been made modular to be easily implemented alongside nearly any distributed system for the sake of enabling testing a breadth of distributed systems.
+Most importantly, though, Redstone's
+determinism allows reproduction of failure conditions,
 allowing developers to confirm, having encountered and debugged a failure,
 that their system will not fail again when confronted by identical conditions.
-Our control over clock functions further allows us to ``accelerate" time,
-increasing ability to test faster, and to emulate the effects of clock jitter.
-Finally, because Redstone is inherently modular,
-it is simple to extend and port to a wider variety of applications and platforms.
+By basing program flow on a pre-chosen seed, any found faults, no matter how improbable, can be reliably replicated.
+We implement and evaluate our framework on a simple system in Linux to demonstrate this determinism in practice.
 
@@
 
+Distributed systems often run on comparatively long time-scales:
+a system may be running for months or years,
+hopefully without failure.
+However,
+it is unrealistic to spend months testing a system to confirm that such durations will not lead to failure.
+But, with control of the machine's time system calls,
+we can effectively "accelerate" time in the test,
+meaning the distributed system to be tested will act as though it has been running for such a duration,
+without interrupting development for such an extended period of time.
+
+Additionally, distributed systems are highly varied,
+and as a result may require features or platform support not foreseen by our implementation.
+Modularity in our design allows our framework to be easily extended,
+not future-proofing it but allowing it to be future-proofed.
+
 Testing offers the ability to confirm that a system can withstand failures.
@@
 
-``Consistently" is another key phrase here,
+``Consistently" is the key phrase here,
 as a test must be replicable.
-% just running the system a few times doesn't confirm that everything that can go wrong has gone wrong.
-As such,
-a good testing system must not only introduce failures,
+A good testing system must not only introduce failures,
 but be able to repeatedly introduce exactly the same failures in exactly the same way.
@@
 ``the only thing worse than a problem that happens all the time is a problem that doesn't happen all the time."
-Therefore, our system must be \textit{deterministic}.
-
-Furthermore,
-distributed systems often run on comparatively long time-scales:
-a system may be running for months or years,
-hopefully without failure.
-However,
-it is unrealistic to spend months testing a system to confirm that such durations will not lead to failure.
-But, with control of the machine's time system calls,
-we can effectively "accelerate" time in the test,
-meaning the distributed system to be tested will act as though it has been running for such a duration,
-without interrupting development for such an extended period of time.
-
-Finally,
-distributed systems are highly varied,
-and as a result may require features or platform support not foreseen by our implementation.
-Modularity in our design allows our framework to be easily extended,
-not future-proofing it but allowing it to be future-proofed.
+Therefore, our system must be \textit{deterministic}. To that end, our system has been designed around deterministic replication of program flow and results.
 
@@
 
+\section{\txtrsdust Randomness and Determinism}
+
+{\fontsize{12}{15}\selectfont
+
+The core of the simulated testing framework is its randomness.
+By introducing randomness into whether or not a network packet is dropped or replayed, for example, the system is able to cover a breadth of inputs that are harder to anticipate when designing the distributed system.
+Many of these inputs will inevitably cause failures in the distributed system due to lack of cases covered by the distributed system itself.
+The whole purpose of distributed systems testing frameworks is to find these cases.
+The primary goal of Redstone though is, in addition to revealing these cases, make it simple to be able to deterministically find these “random” cases.
+The method by which Redstone seeks to do so is by introducing a seed.
+The seed is chosen before the simulator runs by the user.
+Then, rather whenever a random number is called in the simulation (say, 0 if a packet should be dropped or 1 if a packet should be allowed through), the value can be pseudo randomly generated based on the seed.
+Thus, the system covers a “random” program flow that can easily be iterated on.
+When an interesting program flow is discovered by the user, logs are played that cover what occurred during the run.
+However, instead of having to do the analysis entirely in post, the user can take note of the seed with which the simulation was run and simply run it again.
+Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two, the user can expect the exact same program flow to execute and to reproduce the same logs live.
+Between these logs and the replicability of the program flow results, the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.
+
+}
+
+\section{\txtrsdust Evaluations}
+
+{\fontsize{12}{15}\selectfont
+
+This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.
+
+}
+
+\section{\txtrsdust Conclusion}
+
+{\fontsize{12}{15}\selectfont
+
+Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.
+
+// Talk about limitations, otherwise desired future plans/potential future work
+
+}
+
 % Distributed systems are fucking stupid.

### 2024-06-08 paper/paper.tex
Edited determinism section

@@
 We intercept calls to the kernel for the disk and the network, as well as to clock functions,
-introducing our own code. Our control over clock functions further allows us to ``accelerate" time,
+introducing our own code. Our control over clock functions further allows us to
+``accelerate'' time, %NOTE: what the fuck
 increasing ability to test faster, and to emulate the effects of clock jitter.
@@
 {\fontsize{12}{15}\selectfont 
+The core of the simulated testing framework is its test injection.
+By introducing randomness into whether or not a network packet is dropped or replayed,
+for example, the system is able to cover a breadth of ``environmental conditions",
+so to speak,
+that are harder to anticipate when designing the distributed system.
 
-The core of the simulated testing framework is its randomness.
-By introducing randomness into whether or not a network packet is dropped or replayed, for example, the system is able to cover a breadth of inputs that are harder to anticipate when designing the distributed system.
-Many of these inputs will inevitably cause failures in the distributed system due to lack of cases covered by the distributed system itself.
+Many of these ``environmental conditions"
+will inevitably cause failures in the distributed system due to insufficient edge case handling by the implementers of the system.
+This is a feature, not a bug.
 The whole purpose of distributed systems testing frameworks is to find these cases.
-The primary goal of Redstone though is, in addition to revealing these cases, make it simple to be able to deterministically find these “random” cases.
+
+The primary goal of Redstone, however,
+in addition to revealing these cases,
+is to make it simple to be able to deterministically find these “random” cases.
 The method by which Redstone seeks to do so is by introducing a seed.
-The seed is chosen before the simulator runs by the user.
-Then, rather whenever a random number is called in the simulation (say, 0 if a packet should be dropped or 1 if a packet should be allowed through), the value can be pseudo randomly generated based on the seed.
-Thus, the system covers a “random” program flow that can easily be iterated on.
-When an interesting program flow is discovered by the user, logs are played that cover what occurred during the run.
-However, instead of having to do the analysis entirely in post, the user can take note of the seed with which the simulation was run and simply run it again.
-Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two, the user can expect the exact same program flow to execute and to reproduce the same logs live.
-Between these logs and the replicability of the program flow results, the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.
+
+The seed is chosen by the user before the simulator runs.
+Wherever randomness is necessary
+% Then, rather whenever a random number is called in the simulation
+(say, to determine whether a packet should be dropped),
+the value can be pseudo-randomly generated based on the seed.
+
+Thus, the system performs a ``random" and yet totally deterministic program flow,
+which can be used in development for iteration on the tested system.
+When an interesting program flow is discovered by the user,
+instead of just relying on logs after the fact,
+the user can take note of the seed with which the simulation was run and simply run it again.
+
+Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two,
+the user can expect the exact same program flow to execute and to reproduce the same sequence of events as the one they see in their logs.
+Between these logs and the replicability of the program flow results,
+the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.
 
@@
 
-\section{\txtrsdust Evaluations}
+\section{\txtrsdust Evaluation}
 
 {\fontsize{12}{15}\selectfont 
-
-This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.
+\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
+% This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.
 
@@
 {\fontsize{12}{15}\selectfont 
+\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
+% Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.
 
-Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.
-
-// Talk about limitations, otherwise desired future plans/potential future work
+% // Talk about limitations, otherwise desired future plans/potential future work
 
@@
 % understand how their system handles such fucky wuckies
-% A paragraph of text goes here. Lots of text. Plenty of interesting
-% text. Text text text text text text text text text text text text text
-% text text text text text text text text text text text text text text
-% text text text text text text text text text text text text text text
-% text text text text text text text.
-% More fascinating text. Features galore, plethora of promises.
 
 % %-------------------------------------------------------------------------------
-% \section{Footnotes, Verbatim, and Citations}
+% \section*{Acknowledgments}
 % %-------------------------------------------------------------------------------
 % 
-% Footnotes should be places after punctuation characters, without any
-% spaces between said characters and footnotes, like so.%
-% \footnote{Remember that USENIX format stopped using endnotes and is
-% now using regular footnotes.} And some embedded literal code may
-% look as follows.
-% 
-% \begin{verbatim}
-% int main(int argc, char *argv[]) 
-% {
-% return 0;
-% }
-% \end{verbatim}
-% 
-% Now we're going to cite somebody. Watch for the cite tag. Here it
-% comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
-% book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
-% Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
-% about resource management in the ESX hypervisor~\cite{waldspurger02}.
-% 
-% The tilde character (\~{}) in the tex source means a non-breaking
-% space. This way, your reference will always be attached to the word
-% that preceded it, instead of going to the next line.
-% 
-% And the 'cite' package sorts your citations by their numerical order
-% of the corresponding references at the end of the paper, ridding you
-% from the need to notice that, e.g, ``Waldspurger'' appears after
-% ``Arpachi-Dusseau'' when sorting references
-% alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}. 
-% 
-% It'd be nice and thoughtful of you to include a suitable link in each
-% and every bibtex entry that you use in your submission, to allow
-% reviewers (and other readers) to easily get to the cited work, as is
-% done in all entries found in the References section of this document.
-% 
-% Now we're going take a look at Section~\ref{sec:figs}, but not before
-% observing that refs to sections and citations and such are colored and
-% clickable in the PDF because of the packages we've included.
+% The USENIX latex style is old and very tired, which is why
+% there's no \textbackslash{}acks command for you to use when
+% acknowledging. Sorry.
 % 
 % %-------------------------------------------------------------------------------
-% \section{Floating Figures and Lists}
-% \label{sec:figs}
+% \section*{Availability}
 % %-------------------------------------------------------------------------------
-
-% %---------------------------
-% \begin{figure}
-% \begin{center}
-% \begin{tikzpicture}
-% \draw[thin,gray!40] (-2,-2) grid (2,2);
-% \draw[<->] (-2,0)--(2,0) node[right]{$x$};
-% \draw[<->] (0,-2)--(0,2) node[above]{$y$};
-% \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
-% node[anchor=south west]{$\boldsymbol{u}$};
-% \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
-% node[anchor=north east]{$\boldsymbol{-u}$};
-% \end{tikzpicture}
-% \end{center}
-% \caption{\label{fig:vectors} Text size inside figure should be as big as
-% caption's text. Text size inside figure should be as big as
-% caption's text. Text size inside figure should be as big as
-% caption's text. Text size inside figure should be as big as
-% caption's text. Text size inside figure should be as big as
-% caption's text. }
-% \end{figure}
-% %% %---------------------------
-
-% Here's a typical reference to a floating figure:
-% Figure~\ref{fig:vectors}. Floats should usually be placed where latex
-% wants then. Figure\ref{fig:vectors} is centered, and has a caption
-% that instructs you to make sure that the size of the text within the
-% figures that you use is as big as (or bigger than) the size of the
-% text in the caption of the figures. Please do. Really.
 % 
-% In our case, we've explicitly drawn the figure inlined in latex, to
-% allow this tex file to cleanly compile. But usually, your figures will
-% reside in some file.pdf, and you'd include them in your document
-% with, say, \textbackslash{}includegraphics.
-% 
-% Lists are sometimes quite handy. If you want to itemize things, feel
-% free:
-% 
-% \begin{description}
-% 
-% \item[fread] a function that reads from a \texttt{stream} into the
-% array \texttt{ptr} at most \texttt{nobj} objects of size
-% \texttt{size}, returning returns the number of objects read.
-% 
-% \item[Fred] a person's name, e.g., there once was a dude named Fred
-% who separated usenix.sty from this file to allow for easy
-% inclusion.
-% \end{description}
-% 
-% \noindent
-% The noindent at the start of this paragraph in its tex version makes
-% it clear that it's a continuation of the preceding paragraph, as
-% opposed to a new paragraph in its own right.
-% 
-% 
-% \subsection{LaTeX-ing Your TeX File}
-% %-----------------------------------
-% 
-% People often use \texttt{pdflatex} these days for creating pdf-s from
-% tex files via the shell. And \texttt{bibtex}, of course. Works for us.
-
-%-------------------------------------------------------------------------------
-\section*{Acknowledgments}
-%-------------------------------------------------------------------------------
-
-The USENIX latex style is old and very tired, which is why
-there's no \textbackslash{}acks command for you to use when
-acknowledging. Sorry.
-
-%-------------------------------------------------------------------------------
-\section*{Availability}
-%-------------------------------------------------------------------------------
-
-USENIX program committees give extra points to submissions that are
-backed by artifacts that are publicly available. If you made your code
-or data available, it's worth mentioning this fact in a dedicated
-section.
+% USENIX program committees give extra points to submissions that are
+% backed by artifacts that are publicly available. If you made your code
+% or data available, it's worth mentioning this fact in a dedicated
+% section.
 

### 2024-06-08 paper/paper.tex
Updated paper

@@
 {\fontsize{12}{15}\selectfont 
-The core of the simulated testing framework is its test injection.
-By introducing randomness into whether or not a network packet is dropped or replayed,
+The core of the simulated testing framework is its fault injection.
+By randomly (over the randomness of seed generation, rather than just randomly per-run)
+deciding whether a network will drop a packet,
 for example, the system is able to cover a breadth of ``environmental conditions",
@@
 {\fontsize{12}{15}\selectfont 
-\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
+% \texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
 % This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.
+We tested the Redstone system on two benchmark tasks,
+compute and socket.
+The compute task performs a lot of computation and merely confirms that Redstone doesn't get in the way when it isn't called.
+The data seem to back this conclusion.
+The socket task repeatedly opens and closes sockets,
+in effect testing nothing but the overhead of repeated syscalls.
+As such, we see that the overhead on syscalls using Redstone is nearly ten times what it is otherwise.
+However, in the socket task, only about 6 nanoseconds were spent in Redstone proper:
+the rest is the ovehead of using \texttt{ptrace}, a debugging tool,
+as our way of intercepting calls.
+Essentially, we're trying to drive an eighteen-wheeler through the Formula 1.
+
+\textbf{Average User Time}
+\begin{tabular}{|l|r r| r|}
+\hline
+Workload & Linux (ns) &  Redstone (ns) & Ratio \\
+\hline
+Compute & 1,122,191,202 & 1,158,614,972 & 1.0325 \\
+Socket  & 2,333 & 21,804 & 9.3459 \\
+\hline
+\end{tabular}
+
+\begin{figure}[h]
+\includegraphics[width=0.45\textwidth]{redstone_performance.png}
+\caption{Ratio of time to perform benchmark tasks between Redstone and vanilla Linux}
+\end{figure}
 

### 2024-06-08 benches/dgram.cpp
Push simulator implementation work

@@ -1,0 +1,74 @@
+#include <atomic>
+#include <cassert>
+#include <cstring>
+#include <string>
+#include <sys/socket.h>
+#include <sys/un.h>
+#include <thread>
+
+int main() {
+  std::string msg;
+
+  int s1 = socket(AF_UNIX, SOCK_DGRAM, 0);
+  //   int s2 = socket(AF_UNIX, SOCK_DGRAM, 0);
+
+  struct sockaddr_un saddr = {
+      .sun_family = AF_UNIX,
+  };
+  strcpy(saddr.sun_path, "path");
+
+  std::atomic_int remain = 1;
+
+  std::atomic_bool ready = false;
+
+  std::thread t1{
+      [&msg, &ready, &remain]() {
+        int s = socket(AF_UNIX, SOCK_DGRAM, 0);
+
+        assert(0 > bind(s, (sockaddr *)&saddr, sizeof(saddr)));
+
+        ready = true;
+
+        for (;;) {
+          struct sockaddr_storage storage;
+          socklen_t len = sizeof(storage);
+
+          std::string buf;
+          buf.resize(msg.size());
+
+          recvfrom(s, buf.data(), buf.size(), 0, (struct sockaddr *)&storage,
+                   &len);
+
+          if (remain == 0)
+            break;
+        }
+      },
+  };
+
+  std::thread t2{
+      [&msg, &ready, &remain, &saddr]() {
+        int s = socket(AF_UNIX, SOCK_DGRAM, 0);
+
+        while (!ready) {
+        }
+
+        for (;;) {
+          struct sockaddr_storage storage;
+          socklen_t len = sizeof(storage);
+
+          std::string buf;
+          buf.resize(msg.size());
+
+          sendto(s, msg.data(), msg.size(), 0, (struct sockaddr *)&saddr,
+                 sizeof(saddr));
+
+          remain--;
+          if (remain == 0)
+            break;
+        }
+      },
+  };
+
+  t1.join();
+  t2.join();
+}

### 2024-06-08 benches/socket.cpp

@@ -1,0 +1,27 @@
+#include <chrono>
+#include <cstdint>
+#include <cstdio>
+#include <cstdlib>
+#include <iostream>
+#include <sys/socket.h>
+#include <unistd.h>
+
+int main() {
+  const uint64_t iters = 1'000'000;
+
+  const auto start = std::chrono::steady_clock::now();
+
+  for (uint64_t i = 0; i < iters; ++i) {
+    int s = socket(AF_INET, SOCK_DGRAM, 0);
+    close(s);
+  }
+
+  const auto end = std::chrono::steady_clock::now();
+
+  std::cout << "took " << std::chrono::nanoseconds(end - start).count() / iters
+            << "ns per iteration\n";
+
+  return 0;
+}
+// 1121621100
+// 1157662211

### 2024-06-08 demo/demo.h

@@ -1,0 +1,24 @@
+#pragma once
+
+#include <cstdint>
+#include <cstring>
+#include <sys/socket.h>
+#include <sys/un.h>
+#include <system_error>
+
+static constexpr const char *path = "echo-file";
+static constexpr uint64_t iters = 512;
+
+inline sockaddr_un get_addr() {
+  sockaddr_un addr;
+  addr.sun_family = AF_UNIX;
+  // addr.sun_len = 3 + strlen(path);
+  strncpy(addr.sun_path, path, sizeof(addr.sun_path));
+  return addr;
+}
+
+inline void check_return_value(int64_t v) {
+  if (v < 0) {
+    throw std::system_error{errno, std::generic_category()};
+  }
+}

### 2024-06-08 demo/squawk.cpp

@@ -1,0 +1,38 @@
+#include <cstdint>
+#include <string>
+#include <sys/socket.h>
+#include <thread>
+#include <unistd.h>
+
+#include "demo.h"
+
+int main() {
+  int s = socket(AF_UNIX, SOCK_DGRAM, 0);
+  check_return_value(s);
+
+  const auto addr = get_addr();
+  const int flags = 0;
+
+  int64_t i = 0;
+
+  for (;;) {
+    std::string msg = "hello from message ";
+    msg += std::to_string(i);
+    msg += "!";
+
+    int rc = sendto(s, msg.data(), msg.size(), flags,
+                    reinterpret_cast<const sockaddr *>(&addr), sizeof(addr));
+    if (rc < 0) {
+      break;
+    }
+    // check_return_value(rc);
+
+    if (rc == 0) {
+      break;
+    }
+
+    sleep(1);
+
+    i++;
+  }
+}

### 2024-06-08 determinism.py

@@ -1,0 +1,19 @@
+import subprocess
+import hashlib
+
+RUNS = 100
+args = ["./build/redstone", "sim.toml"]
+
+sha = None
+
+for _ in range(RUNS):
+    result = subprocess.run(args, stdout=subprocess.PIPE)
+    result.check_returncode()
+
+    print("finished run!")
+
+    iter_sha = hashlib.sha256(result.stdout)
+    if sha is None:
+        sha = iter_sha
+    if sha != iter_sha:
+        print("run had different sha")

### 2024-06-08 src/hook/hook.cpp

@@ -59,12 +59,17 @@ static std::vector<hook> build_hook_table() {
       {SYS_write, sys_write},
       {SYS_read, sys_read},
       {SYS_close, sys_close},
+      {SYS_socket, sys_socket},
+      {SYS_sendto, sys_sendto},
+      {SYS_recvfrom, sys_recvfrom},
+      {SYS_connect, sys_connect},
+      {SYS_bind, sys_bind},
+      {SYS_clock_gettime, sys_clock_gettime},
+      {SYS_clock_nanosleep, sys_clock_nanosleep},
   };
 
   for (auto passthrough : passthroughs) {
     std::pair<uint64_t, hook> pair{passthrough, explicit_passthrough};
-
-    fmt::println("passthrough {}", syscall_name(passthrough));
     map.push_back(pair);
   }
 

### 2024-06-08 src/hook/hook.hpp

@@ -51,7 +51,7 @@ struct hook_result {
       : kind{hook_result_kind::handled}, handled{h.result} {}
   hook_result(error e)
       : kind{hook_result_kind::handled},
-        handled{static_cast<uint64_t>(e.cerrno)} {
+        handled{static_cast<uint64_t>(-e.cerrno)} {
     assert(0 <= e.cerrno);
   }
 };

### 2024-06-08 src/hook/impls.cpp

@@ -1,17 +1,109 @@
 #include "impls.hpp"
+#include "hook.hpp"
+#include "metrics.hpp"
+#include "net/datagram_socket.hpp"
+#include "net/socket.hpp"
+#include "net/stream_socket.hpp"
 #include "sim/replica.hpp"
 
 #include <cassert>
 #include <cerrno>
+#include <chrono>
+#include <cstddef>
 #include <cstdint>
 #include <cstdio>
+#include <cstring>
+#include <ctime>
 #include <memory>
+#include <netinet/ip.h>
+#include <span>
 #include <spdlog/spdlog.h>
+#include <sys/socket.h>
+#include <sys/un.h>
+#include <system_error>
+#include <thread>
 #include <unistd.h>
+#include <vector>
 
 namespace redstone::hook {
 namespace {
-void fd_write() {}
+auto store_fragment_callback(sim::replica &replica, uintptr_t addr) {
+  return [&replica, addr](auto fragment) mutable {
+    auto &runner = replica.runner();
+    auto res = runner.read_memory(addr, fragment);
+    if (0 <= res) {
+      addr += res;
+    }
+    return res;
+  };
+}
+
+auto load_fragment_callback(sim::replica &replica, uintptr_t addr) {
+  return [&replica, addr](auto fragment) mutable {
+    auto &runner = replica.runner();
+    auto res = runner.write_memory(addr, fragment);
+    if (0 <= res) {
+      addr += res;
+    }
+    return res;
+  };
+}
+
+net::socket_addr parse_addr(sim::replica &replica, uintptr_t dest_addr,
+                            size_t dest_len, std::error_code &err) {
+  err = {};
+
+  struct sockaddr_storage addr_storage;
+
+  if (sizeof(addr_storage) < dest_len || dest_len < 2) {
+    err = std::error_code{EINVAL, std::generic_category()};
+    return {};
+  }
+
+  std::vector<std::byte> dest{dest_len, std::byte{}};
+  if (0 > replica.runner().read_memory(dest_addr, dest)) {
+    err = std::error_code{EFAULT, std::generic_category()};
+    return {};
+  }
+
+  memcpy(&addr_storage, dest.data(), dest.size());
+
+  net::address_family af;
+
+  switch (addr_storage.ss_family) {
+  case AF_INET: {
+    auto in_addr = reinterpret_cast<const sockaddr_in *>(&addr_storage);
+    net::ipv4_addr ip_addr{};
+
[…]

### 2024-06-08 src/hook/impls.hpp

@@ -1,6 +1,7 @@
 #pragma once
 
 #include "hook.hpp"
+#include <span>
 
 namespace redstone::hook {
 hook_result sys_write(sim::replica &replica,
@@ -9,4 +10,22 @@ hook_result sys_read(sim::replica &replica,
                      std::span<const std::uint64_t, 6> args);
 hook_result sys_close(sim::replica &replica,
                       std::span<const std::uint64_t, 6> args);
+hook_result sys_open(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_socket(sim::replica &replica,
+                       std::span<const std::uint64_t, 6> args);
+hook_result sys_sendto(sim::replica &replica,
+                       std::span<const std::uint64_t, 6> args);
+hook_result sys_recvfrom(sim::replica &replica,
+                         std::span<const std::uint64_t, 6> args);
+hook_result sys_connect(sim::replica &replica,
+                        std::span<const std::uint64_t, 6> args);
+hook_result sys_read(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_bind(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_clock_gettime(sim::replica &replica,
+                              std::span<const std::uint64_t, 6> args);
+hook_result sys_clock_nanosleep(sim::replica &replica,
+                                std::span<const std::uint64_t, 6> args);
 } // namespace redstone::hook

### 2024-06-08 src/main.cpp

@@ -1,121 +1,188 @@
-
-
-#include <sys/syscall.h>
-
-#include <bitset>
+#include <chrono>
+#include <csignal>
 #include <cstdio>
-
 #include <fmt/format.h>
+#include <map>
+#include <memory>
 #include <spdlog/spdlog.h>
+#include <stdexcept>
+#include <sys/random.h>
+#include <sys/syscall.h>
+#include <thread>
+#include <toml++/toml.hpp>
+#include <vector>
 
 #include "hook/hook.hpp"
-#include "hook/syscalls.hpp"
-#include "random/splitmix.hpp"
-#include "redstone.hpp"
+#include "metrics.hpp"
 #include "sim/machine.hpp"
 #include "sim/simulator.hpp"
 
-namespace {
-constexpr int passthroughs[] = {
-    14,  // rt_sigprocmask
-    59,  // execve
-    12,  // brk
-    158, // arch_prctl
-    9,   // mmap
-    10,  // mprotect
-    11,  // munmap
-    39,  // getpid
-    231, // exit_group
-};
-std::bitset<500> get_passthroughs() {
-  std::bitset<500> all;
-
-  for (int sysno : passthroughs) {
-    all.set(sysno);
-  }
-
-  return all;
+uint64_t random_seed() {
+  uint64_t buf;
+  getrandom(&buf, sizeof(buf), 0);
+  return buf;
 }
-} // namespace
 
-struct logging_handler : redstone::hook::handlers {
-  std::bitset<500> passthrough = get_passthroughs();
-
-  std::optional<std::uint64_t>
-  maybe_handle(std::uint64_t sysno,
-               std::span<const uint64_t, 6> args) override {
-    if (should_passthrough(sysno)) {
-      fmt::println("passthrough: {} ({})", sysno,
-                   redstone::hook::syscall_name(sysno));
-      return std::nullopt;
-    }
-
-    if (sysno == SYS_write && args[0] == 1) {
-      uintptr_t ptr = args[1];
-      size_t len = args[2];
-      fmt::println("write stdout ptr = {}, len = {}", (void *)ptr, len);
-      return len;
-    }
-
-    auto name = redstone::hook::syscall_name(sysno);
-    spdlog::warn("unhandled: {} ({})", sysno, name);
-    return std::nullopt;
-  }
-
-  void exited(int status) override { fmt::println("exited: {}", status); }
-
-private:
-  bool should_passthrough(std::uint64_t sysno) const {
[…]

### 2024-06-08 src/metrics.hpp

@@ -1,0 +1,51 @@
+#pragma once
+
+#include <atomic>
+#include <chrono>
+#include <cstdint>
+
+namespace redstone::metrics {
+struct metric;
+
+struct timed {
+  ~timed() { stop(); }
+
+  void stop();
+
+  metric *m;
+  std::chrono::high_resolution_clock::time_point start;
+};
+
+struct metric {
+  std::atomic<std::uint64_t> total_time = 0;
+  std::atomic<std::uint64_t> count = 0;
+
+  timed start() {
+    auto now = std::chrono::high_resolution_clock::now();
+    return timed{this, now};
+  }
+
+  void add_sample(std::chrono::nanoseconds sample) {
+    total_time += sample.count();
+    count += 1;
+  }
+
+  std::chrono::nanoseconds average() const {
+    return std::chrono::nanoseconds{total_time / count};
+  }
+};
+
+inline void timed::stop() {
+  auto end = std::chrono::high_resolution_clock::now();
+  auto sample = start - end;
+  if (m != nullptr) {
+    m->add_sample(sample);
+  }
+  m = nullptr;
+}
+
+static metric sys_socket;
+static metric sys_close;
+
+void dump();
+} // namespace redstone::metrics

### 2024-06-08 src/net/datagram_socket.cpp

@@ -1,0 +1,119 @@
+#include "datagram_socket.hpp"
+#include <cerrno>
+#include <cstdio>
+#include <fmt/format.h>
+#include <memory>
+#include <random>
+#include <vector>
+
+namespace redstone::net {
+void datagram_pipe::send(std::vector<std::byte> data, socket_addr from) {
+  assert(data.size() < max_udp_packet_size);
+
+  if (fault_options_.should_drop(rng_))
+    return;
+
+  const auto now = std::chrono::steady_clock::now();
+  const auto latency = fault_options_.latency(rng_);
+  const auto arrival = now + latency;
+
+  packet p{
+      .arrival = arrival,
+      .bytes = std::move(data),
+      .from = std::move(from),
+  };
+
+  std::vector<packet> replays;
+  const auto replay_count = fault_options_.replay_count(rng_);
+  replays.reserve(replay_count);
+
+  while (replays.size() < replay_count) {
+    replays.push_back(p);
+    replays.back().arrival = now + fault_options_.latency(rng_) * 2;
+  }
+
+  std::unique_lock lock{mutex_};
+
+  packets_.push(std::move(p));
+  for (auto &replay : replays) {
+    packets_.push(std::move(replay));
+  }
+
+  cond_.notify_one();
+  lock.unlock();
+}
+
+std::pair<std::vector<std::byte>, socket_addr> datagram_pipe::recv() {
+  std::unique_lock lock{mutex_};
+
+  while (true) {
+    if (packets_.empty()) {
+      cond_.wait(lock);
+      continue;
+    }
+
+    auto &p = packets_.top();
+
+    if (p.arrival > std::chrono::steady_clock::now()) {
+      cond_.wait_until(lock, p.arrival);
+      continue;
+    }
+
+    auto data = std::move(p.bytes);
+    auto addr = std::move(p.from);
+    packets_.pop();
+    return {data, addr};
+  }
+}
+
+void datagram_socket::deliver(std::vector<std::byte> dgram, socket_addr addr) {
+  std::unique_lock lock{mutex_};
+  inbound_.send(std::move(dgram), std::move(addr));
+}
+
+std::int64_t datagram_socket::send_to(
+    tl::function_ref<int(std::span<std::byte>)> read_data_callback,
+    std::size_t bytes, const socket_addr &dst) {
+  auto sock = net_->get(dst);
+  if (!sock) {
[…]

### 2024-06-08 src/net/datagram_socket.hpp

@@ -1,0 +1,95 @@
+#pragma once
+
+#include <chrono>
+#include <condition_variable>
+#include <cstddef>
+#include <cstdint>
+#include <mutex>
+#include <queue>
+#include <span>
+#include <vector>
+
+#include "fault.hpp"
+#include "network.hpp"
+#include "random/xoshiro.hpp"
+#include "sim/simulator.hpp"
+#include "socket.hpp"
+
+namespace redstone::net {
+// A one-way UDP stream
+class datagram_pipe {
+public:
+  explicit datagram_pipe(const net_fault_options &fault_options)
+      : fault_options_{fault_options} {}
+
+  void send(std::vector<std::byte> packet, socket_addr from);
+  std::pair<std::vector<std::byte>, socket_addr> recv();
+
+  template <typename Rng>
+  void seed(Rng &rng) {
+    rng_.seed_from(rng);
+  }
+
+private:
+  struct packet {
+    std::chrono::steady_clock::time_point arrival;
+    std::vector<std::byte> bytes;
+    mutable std::size_t consumed = 0;
+    socket_addr from;
+
+    friend bool operator<(const packet &lhs, const packet &rhs) {
+      // Flip ordering
+      return lhs.arrival > rhs.arrival;
+    }
+
+    friend bool operator>(const packet &lhs, const packet &rhs) {
+      return rhs < lhs;
+    }
+
+    friend bool operator<=(const packet &lhs, const packet &rhs) {
+      return !(rhs < lhs);
+    }
+
+    friend bool operator>=(const packet &lhs, const packet &rhs) {
+      return !(lhs < rhs);
+    }
+
+    std::span<const std::byte> remaining() const {
+      std::span<const std::byte> data = bytes;
+      return data.subspan(consumed);
+    }
+  };
+
+  std::mutex mutex_;
+  std::condition_variable cond_;
+  std::priority_queue<packet> packets_;
+
+  const net_fault_options fault_options_{};
+
+  // Only accessed by writer
+  random::xoshiro256_star_star rng_;
+
+  void send_packet(std::span<const std::byte> packet);
+  packet recv_packet();
+};
+
+class datagram_socket : public socket {
+public:
+  explicit datagram_socket(address_family af, sim::simulator &sim);
+
+  std::int64_t
+  send_to(tl::function_ref<int(std::span<std::byte>)> read_data_callback,
+          std::size_t bytes, const socket_addr &dst);
+
[…]

### 2024-06-08 src/net/fault.hpp

@@ -1,6 +1,8 @@
 #pragma once
 
 #include <chrono>
+#include <cstdio>
+#include <random>
 
 #include "random/rng.hpp"
 
@@ -19,7 +21,8 @@ struct net_fault_options {
 
   template <typename Rng>
   bool should_drop(Rng &&rng) const {
-    return random::gen_bool(rng, p_drop);
+    std::bernoulli_distribution dis{p_drop};
+    return dis(rng);
   }
 
   template <typename Rng>

### 2024-06-08 src/net/network.cpp

@@ -1,0 +1,39 @@
+#include "network.hpp"
+#include <cerrno>
+#include <system_error>
+
+namespace redstone::net {
+std::error_code network::bind(socket_addr addr, std::shared_ptr<socket> sock) {
+  std::unique_lock lock{mutex_};
+
+  auto &slot = map_[addr];
+
+  if (slot.lock() != nullptr) {
+    return std::error_code{EADDRNOTAVAIL, std::generic_category()};
+  }
+
+  slot = sock;
+  return {};
+}
+
+void network::clear(const socket_addr &addr, socket *s) {
+  std::unique_lock lock{mutex_};
+
+  auto it = map_.find(addr);
+
+  if (it == map_.end()) {
+    return;
+  }
+
+  auto p = it->second.lock();
+  if (p != nullptr && p.get() != s)
+    return;
+
+  map_.erase(it);
+}
+
+std::shared_ptr<socket> network::get(const socket_addr &addr) {
+  std::unique_lock lock{mutex_};
+  return map_[addr].lock();
+}
+} // namespace redstone::net

### 2024-06-08 src/net/socket.hpp

@@ -1,0 +1,108 @@
+#pragma once
+
+#include "sim/file_descriptor.hpp"
+
+#include <cstddef>
+#include <cstdint>
+#include <cstring>
+#include <functional>
+#include <span>
+#include <string>
+#include <variant>
+
+namespace redstone::net {
+enum address_family {
+  ipv4,
+  unix_,
+};
+
+struct ipv4_addr {
+  uint16_t port;
+  char octets[4];
+
+  friend bool operator<(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    if (memcmp(lhs.octets, rhs.octets, 4) < 0)
+      return true;
+    return lhs.port < rhs.port;
+  }
+
+  friend bool operator>(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    return rhs < lhs;
+  }
+  friend bool operator<=(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    return !(rhs < lhs);
+  }
+  friend bool operator>=(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    return !(lhs < rhs);
+  }
+
+  friend bool operator==(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    return lhs.port == rhs.port && memcmp(lhs.octets, rhs.octets, 4) == 0;
+  }
+  friend bool operator!=(const ipv4_addr &lhs, const ipv4_addr &rhs) {
+    return !(lhs == rhs);
+  }
+};
+
+struct unix_addr {
+  std::string path;
+
+  friend bool operator<(const unix_addr &lhs, const unix_addr &rhs) {
+    return lhs.path < rhs.path;
+  }
+  friend bool operator>(const unix_addr &lhs, const unix_addr &rhs) {
+    return rhs < lhs;
+  }
+  friend bool operator<=(const unix_addr &lhs, const unix_addr &rhs) {
+    return !(rhs < lhs);
+  }
+  friend bool operator>=(const unix_addr &lhs, const unix_addr &rhs) {
+    return !(lhs < rhs);
+  }
+
+  friend bool operator==(const unix_addr &lhs, const unix_addr &rhs) {
+    return lhs.path == rhs.path;
+  }
+  friend bool operator!=(const unix_addr &lhs, const unix_addr &rhs) {
+    return !(lhs == rhs);
+  }
+};
+
+using socket_addr = std::variant<ipv4_addr, unix_addr>;
+
+enum class socket_type {
+  stream,
[…]

### 2024-06-08 src/net/udp.cpp

@@ -1,93 +1,133 @@
-#include "net/udp.hpp"
+// #include "net/udp.hpp"
 
-#include <algorithm>
-#include <chrono>
-#include <cstddef>
-#include <cstdint>
-#include <limits>
-#include <span>
-#include <vector>
+// #include <algorithm>
+// #include <chrono>
+// #include <cstddef>
+// #include <cstdint>
+// #include <limits>
+// #include <span>
+// #include <vector>
 
-constexpr std::size_t max_udp_packet_size =
-    std::numeric_limits<uint16_t>::max() - 128;
+// constexpr std::size_t max_udp_packet_size =
+//     std::numeric_limits<uint16_t>::max() - 128;
 
-namespace redstone::net {
-std::int64_t udp_stream::write(std::span<const std::byte> data) {
-  if (max_udp_packet_size < data.size_bytes())
-    data = data.subspan(0, max_udp_packet_size);
+// namespace redstone::net {
+// std::int64_t udp_stream::write(std::span<const std::byte> data) {
+//   if (max_udp_packet_size < data.size_bytes())
+//     data = data.subspan(0, max_udp_packet_size);
 
-  if (fault_options_.should_drop(rng_))
-    return data.size();
+//   if (fault_options_.should_drop(rng_))
+//     return data.size();
 
-  const auto now = std::chrono::steady_clock::now();
-  const auto latency = fault_options_.latency(rng_);
-  const auto arrival = now + latency;
+//   const auto now = std::chrono::steady_clock::now();
+//   const auto latency = fault_options_.latency(rng_);
+//   const auto arrival = now + latency;
 
-  udp_packet p{
-      .arrival = arrival,
-      .bytes = std::vector<std::byte>{data.begin(), data.end()},
-  };
+//   udp_packet p{
+//       .arrival = arrival,
+//       .bytes = std::vector<std::byte>{data.begin(), data.end()},
+//   };
 
-  std::vector<udp_packet> replays;
-  const auto replay_count = fault_options_.replay_count(rng_);
-  replays.reserve(replay_count);
+//   std::vector<udp_packet> replays;
+//   const auto replay_count = fault_options_.replay_count(rng_);
+//   replays.reserve(replay_count);
 
-  while (replays.size() < replay_count) {
-    replays.push_back(p);
-    replays.back().arrival = now + fault_options_.latency(rng_);
-  }
+//   while (replays.size() < replay_count) {
[…]

### 2024-06-08 src/net/udp.hpp

@@ -1,70 +1,73 @@
-#pragma once
+// #pragma once
 
-#include <chrono>
-#include <condition_variable>
-#include <cstddef>
-#include <cstdint>
-#include <functional>
-#include <mutex>
-#include <queue>
-#include <span>
-#include <vector>
+// #include <chrono>
+// #include <condition_variable>
+// #include <cstddef>
+// #include <cstdint>
+// #include <functional>
+// #include <mutex>
+// #include <queue>
+// #include <span>
+// #include <vector>
 
-#include "fault.hpp"
-#include "random/xoshiro.hpp"
+// #include "fault.hpp"
+// #include "random/xoshiro.hpp"
 
-namespace redstone::net {
-// A one-way UDP stream
-class udp_stream {
-public:
-  std::int64_t write(std::span<const std::byte> packet);
-  std::int64_t read(std::span<std::byte> buf);
+// namespace redstone::net {
+// // A one-way UDP stream
+// class datagram_pipe {
+// public:
+//   void send(std::vector<std::byte> packet);
+//   std::vector<std::byte> recv();
 
-private:
-  struct udp_packet {
-    std::chrono::steady_clock::time_point arrival;
-    std::vector<std::byte> bytes;
-    mutable std::size_t consumed = 0;
+//   std::int64_t write(std::span<const std::byte> packet);
+//   std::int64_t read(std::span<std::byte> buf);
 
-    friend bool operator<(const udp_packet &lhs, const udp_packet &rhs) {
-      // Flip ordering
-      return lhs.arrival > rhs.arrival;
-    }
+// private:
+//   struct packet {
+//     std::chrono::steady_clock::time_point arrival;
+//     std::vector<std::byte> bytes;
+//     mutable std::size_t consumed = 0;
 
-    friend bool operator>(const udp_packet &lhs, const udp_packet &rhs) {
-      return rhs < lhs;
-    }
+//     friend bool operator<(const packet &lhs, const packet &rhs) {
+//       // Flip ordering
+//       return lhs.arrival > rhs.arrival;
+//     }
 
-    friend bool operator<=(const udp_packet &lhs, const udp_packet &rhs) {
-      return !(rhs < lhs);
-    }
+//     friend bool operator>(const packet &lhs, const packet &rhs) {
+//       return rhs < lhs;
+//     }
 
-    friend bool operator>=(const udp_packet &lhs, const udp_packet &rhs) {
-      return !(lhs < rhs);
-    }
[…]

### 2024-06-08 src/redstone.cpp

@@ -1,58 +1,0 @@
-#include "redstone.hpp"
-
-#include <spdlog/spdlog.h>
-#include <vector>
-
-#include "hook/hook.hpp"
-#include "random/splitmix.hpp"
-
-namespace redstone {
-simulator::simulator(uint64_t seed) {
-  spdlog::trace("construct new simulator with seed {:#x}", seed);
-
-  random::split_mix splitmix{seed};
-  root_rng_.seed_from(splitmix);
-}
-
-instance &simulator::push_instance(std::string path) {
-  std::scoped_lock _lock{sim_mutex_};
-
-  instances_.push_back(instance{.path = std::move(path)});
-
-  instance &i = instances_.back();
-  i.args.push_back(i.path);
-  i.rng.seed_from(root_rng_);
-
-  return i;
-}
-
-namespace {
-struct handlers : hook::handlers {
-  std::optional<std::uint64_t>
-  maybe_handle(std::uint64_t sysno, std::span<const uint64_t, 6> args) final {
-    return std::nullopt;
-  }
-};
-
-// Handles running a single instance
-void run_instance(simulator &sim, instance &self) {
-  hook::command command{
-      .path = self.path,
-      .args = self.args,
-      .env = self.env,
-  };
-}
-} // namespace
-
-void simulator::run() {
-  std::vector<std::thread> running;
-
-  for (auto &i : instances_) {
-    running.emplace_back([this, &i] { run_instance(*this, i); });
-  }
-
-  for (auto &thread : running) {
-    thread.join();
-  }
-}
-} // namespace redstone

### 2024-06-08 src/redstone.hpp

@@ -1,66 +1,0 @@
-#pragma once
-
-#include <cstdint>
-#include <cstdio>
-#include <cstdlib>
-#include <memory>
-#include <mutex>
-#include <thread>
-#include <vector>
-
-#include "random/xoshiro.hpp"
-#include "sim/runner.hpp"
-#include "sys/child.hpp"
-
-namespace redstone {
-struct child {
-  sys::child process;
-  std::thread thread;
-};
-
-struct instance_metrics {
-  uint64_t crashes_forced = 0;
-  uint64_t crashes_bugs = 0;
-};
-
-struct instance {
-  // Should be initialized
-
-  std::string path;
-  std::vector<std::string> args;
-  std::vector<std::string> env;
-  random::xoshiro256_star_star rng;
-
-  // Can be default initialized
-  std::shared_ptr<child> child;
-  instance_metrics metrics;
-
-  ~instance() {
-    if (child) {
-      std::fputs("instance destroyed while child running", stderr);
-      std::abort();
-    }
-  }
-};
-
-class simulator {
-public:
-  explicit simulator(uint64_t seed);
-
-  instance &push_instance(std::string path);
-
-  void run();
-
-private:
-  std::mutex sim_mutex_;
-
-  // Root rng that all other seeds are generated from
-  random::xoshiro256_star_star root_rng_;
-
-  // A vector of instances, some running some not
-  std::vector<instance> instances_;
-
-  // Fuck you dave
-  void dave_tripped_on_a_power_cable();
-};
-} // namespace redstone

### 2024-06-08 src/replica.cpp

@@ -1,77 +1,0 @@
-#include "replica.hpp"
-
-#include <sys/syscall.h>
-
-#include <cassert>
-#include <cstdint>
-#include <map>
-#include <memory>
-#include <optional>
-#include <span>
-#include <variant>
-#include <vector>
-
-#include "hook/hook.hpp"
-
-namespace redstone::replica {
-using file_descriptor = std::variant<disk::open_file>;
-
-struct child {
-  sys::child process;
-  std::map<int, std::shared_ptr<file_descriptor>> fds;
-};
-
-replica::~replica() = default;
-
-namespace {
-constexpr unsigned explicit_passthroughs[] = {SYS_mmap};
-
-std::optional<std::uint64_t> passthrough(std::span<const std::uint64_t, 6>) {
-  return std::nullopt;
-}
-
-class hook_handlers : redstone::hook::handlers {
-public:
-  using hook =
-      std::optional<std::uint64_t> (*)(std::span<const std::uint64_t, 6>);
-
-  explicit hook_handlers(child *child, replica *replica)
-      : child_{child}, replica_{replica} {
-
-    for (auto sysno : explicit_passthroughs) {
-      set_explicit_passthrough(sysno);
-    }
-  }
-
-  std::optional<std::uint64_t>
-  maybe_handle(std::uint64_t sysno, std::span<const uint64_t, 6> args) final {
-    if (sysno < hooks_table_.size()) {
-      auto hook = hooks_table_[sysno];
-
-      if (hook != nullptr) {
-        return hook(args);
-      }
-    }
-    return std::nullopt;
-  }
-
-  void set_explicit_passthrough(unsigned sysno) {
-    set_handler(sysno, passthrough);
-  }
-
-  void set_handler(unsigned sysno, hook handler) {
-    assert(handler != nullptr);
-
-    if (hooks_table_.size() <= sysno) {
-      hooks_table_.resize(sysno);
-    }
-    hooks_table_.at(sysno) = handler;
-  }
-
-private:
-  std::vector<hook> hooks_table_;
-  child *child_;
-  replica *replica_;
-};
-} // namespace
-} // namespace redstone::replica

### 2024-06-08 src/replica.hpp

@@ -1,17 +1,0 @@
-#pragma once
-
-#include <memory>
-
-#include "disk/disk.hpp"
-#include "sys/child.hpp"
-#include "sys/command.hpp"
-
-namespace redstone::replica {
-struct child;
-
-struct replica {
-  std::unique_ptr<child> child;
-
-  ~replica();
-};
-} // namespace redstone::replica

### 2024-06-08 src/sim/file_descriptor.cpp

@@ -5,6 +5,7 @@
 #include <cstddef>
 #include <memory>
 #include <spdlog/spdlog.h>
+#include <string_view>
 #include <vector>
 
 namespace redstone::sim {
@@ -68,6 +69,8 @@ public:
 
     std::size_t done = 0;
 
+    fmt::println("output: '{}'", std::string_view{(const char *)buf.data(), 4});
+
     while (done < bytes) {
       std::span tmp = buf;
 
@@ -75,14 +78,16 @@ public:
         tmp = tmp.subspan(0, bytes);
       }
 
-      spdlog::trace("f1");
       auto res = load(tmp);
-      spdlog::trace("f2");
       if (res < 0) {
         return res;
       }
 
-      std::fwrite(tmp.data(), 1, tmp.size_bytes(), stdout);
+      fmt::println("output: '{}'",
+                   std::string_view{(const char *)tmp.data(), tmp.size()});
+
+      fmt::println("output: {}",
+                   std::fwrite(tmp.data(), 1, tmp.size_bytes(), stdout));
 
       done += tmp.size_bytes();
     }

### 2024-06-08 src/sim/machine.cpp

@@ -4,6 +4,6 @@ namespace redstone::sim {
 void machine::start() {
   runner_options_.machine = this;
   auto handle = runner_(runner_options_);
-  current_ = std::make_shared<replica>(handle, this);
+  current_ = std::make_shared<replica>(handle, *this);
 }
 } // namespace redstone::sim

### 2024-06-08 src/sim/machine.hpp

@@ -5,21 +5,28 @@
 
 #include "replica.hpp"
 #include "runner.hpp"
+#include "simulator.hpp"
 
 namespace redstone::sim {
+class simulator;
+
 class machine {
 public:
-  explicit machine(runner_options options)
-      : runner_options_{std::move(options)} {}
+  explicit machine(simulator &sim, runner_options options)
+      : sim_{&sim}, runner_options_{std::move(options)} {}
 
   std::shared_ptr<replica> current_replica() { return current_; }
 
   void start();
+
+  sim::simulator &sim() { return *sim_; }
 
 private:
   runner_options runner_options_;
   std::shared_ptr<replica> current_;
   std::function<std::shared_ptr<runner_handle>(const runner_options &)> runner_{
       ptrace_run};
+  sim::simulator *sim_;
+  net::network *net_;
 };
 } // namespace redstone::sim

### 2024-06-08 src/sim/replica.cpp

@@ -1,9 +1,15 @@
 #include "replica.hpp"
+#include "machine.hpp"
+#include "simulator.hpp"
 #include <memory>
 
 namespace redstone::sim {
 replica::~replica() = default;
 
-replica::replica(std::shared_ptr<runner_handle> handle, machine *m)
-    : handle_{std::move(handle)}, machine_{m} {}
+replica::replica(std::shared_ptr<runner_handle> handle, machine &m)
+    : handle_{std::move(handle)}, machine_{&m} {}
+
+net::network &replica::network() { return machine_->sim().net(); }
+
+simulator &replica::sim() { return machine_->sim(); }
 } // namespace redstone::sim

### 2024-06-08 src/sim/replica.hpp

@@ -1,16 +1,23 @@
 #pragma once
 
 #include "file_descriptor.hpp"
+#include "net/network.hpp"
 #include "runner.hpp"
+
 #include <cassert>
+#include <chrono>
 #include <memory>
 
 namespace redstone::sim {
+using clock = std::chrono::steady_clock;
+
+class simulator;
+
 class replica {
 public:
   ~replica();
 
-  explicit replica(std::shared_ptr<runner_handle> handle, machine *m);
+  explicit replica(std::shared_ptr<runner_handle> handle, machine &m);
 
   file_descriptor_table &fd_table() { return fd_table_; }
 
@@ -19,9 +26,17 @@ public:
     return *handle_;
   }
 
+  net::network &network();
+
+  simulator &sim();
+
+  clock::time_point epoch() const { return epoch_; }
+
 private:
   std::shared_ptr<runner_handle> handle_;
   machine *machine_ = nullptr;
+  net::network *net_;
   file_descriptor_table fd_table_;
+  const clock::time_point epoch_ = clock::now();
 };
 } // namespace redstone::sim

### 2024-06-08 src/sim/runner.hpp

@@ -22,7 +22,6 @@ struct runner_options {
   std::string path;
   std::vector<std::string> args;
   std::vector<std::string> env;
-  simulator *simulator;
   machine *machine;
 };
 

### 2024-06-08 src/sim/runner/ptrace.cpp

@@ -1,5 +1,21 @@
 #include "sim/runner.hpp"
 
+#include <cassert>
+#include <cerrno>
+#include <chrono>
+#include <condition_variable>
+#include <csignal>
+#include <cstddef>
+#include <cstdint>
+#include <cstdio>
+#include <cstring>
+#include <fcntl.h>
+#include <iostream>
+#include <memory>
+#include <mutex>
+#include <optional>
+#include <span>
+#include <stdexcept>
 #include <sys/auxv.h>
 #include <sys/prctl.h>
 #include <sys/ptrace.h>
@@ -8,18 +24,9 @@
 #include <sys/types.h>
 #include <sys/user.h>
 #include <sys/wait.h>
-#include <unistd.h>
-
-#include <condition_variable>
-#include <csignal>
-#include <cstdint>
-#include <memory>
-#include <mutex>
-#include <optional>
-#include <span>
-#include <stdexcept>
 #include <system_error>
 #include <thread>
+#include <unistd.h>
 #include <variant>
 #include <vector>
 
@@ -34,6 +41,38 @@
 #include "sys/ptrace.hpp"
 
 namespace redstone::sim {
+
+class barrier {
+public:
+  explicit barrier(std::size_t count) : count_{count} {}
+
+  void wait() {
+    std::unique_lock lock{mutex_};
+    assert(current_ != 0);
+
+    current_--;
+
+    if (current_ == 0) {
+      current_ = count_;
+      epoch_++;
+      cond_.notify_all();
+      return;
+    }
+
+    auto epoch = epoch_;
+
+    while (epoch == epoch_) {
+      cond_.wait(lock);
+    }
+  }
+
+private:
+  std::size_t count_;
+  std::size_t current_ = count_;
+  std::size_t epoch_ = 0;
+  std::mutex mutex_;
+  std::condition_variable cond_;
+};
 namespace {
 sys::child spawn(const runner_options &options) {
   if (options.args.at(0) != options.path) {
@@ -75,7 +114,6 @@ sys::child spawn(const runner_options &options) {
 }
 
 void replace_syscall_with_result(sys::child &child, uint64_t result) {
-
   // Overwrite syscall with SYS_gettid (noop, essentially)
   auto regs = sys::ptrace::get_regs(child);
   regs.orig_rax = SYS_gettid;
@@ -108,21 +146,15 @@ void handle_trapped(sys::child &child, replica &replica) {
     return;
   }
 
[…]

### 2024-06-08 src/sim/simulator.hpp

@@ -1,15 +1,39 @@
 #pragma once
 
+#include <array>
+#include <cstdint>
+#include <utility>
 #include <vector>
 
 #include "machine.hpp"
+#include "net/fault.hpp"
+#include "random/splitmix.hpp"
 #include "random/xoshiro.hpp"
 
 namespace redstone::sim {
+struct options {
+  net::net_fault_options net_faults{};
+  double time_scale = 1.0;
+  std::uint64_t seed;
+};
+
 class simulator {
 public:
+  explicit simulator(options &&o) : options_{std::move(o)} {
+    random::split_mix seed_source{options_.seed};
+    rng_.seed_from(seed_source);
+  }
+
+  net::network &net() { return net_; }
+
+  random::xoshiro256_star_star &rng() { return rng_; }
+
+  const options &initial_options() const { return options_; }
+
 private:
   random::xoshiro256_star_star rng_;
   std::vector<machine> machines_;
+  net::network net_;
+  options options_;
 };
 } // namespace redstone::sim

### 2024-06-08 src/simple.cpp

@@ -1,10 +1,18 @@
+#include <cassert>
 #include <cstdio>
 #include <ctime>
 #include <sqlite3.h>
 #include <stdexcept>
+#include <sys/socket.h>
+#include <unistd.h>
 
 int main() {
+  int s = socket(AF_INET, SOCK_DGRAM, 0);
+  assert(s > 0);
+  ::close(s);
+
   printf("hi!\n");
+  return 0;
 
   struct timespec tm;
   clock_gettime(CLOCK_BOOTTIME, &tm);

### 2024-06-08 src/sys/file.cpp

@@ -1,15 +1,60 @@
 #include "file.hpp"
+#include "child.hpp"
+#include <cassert>
 #include <cerrno>
+#include <cstdio>
+#include <fcntl.h>
+#include <fmt/core.h>
+#include <system_error>
 #include <unistd.h>
 
 namespace redstone::sys {
+std::uint64_t file::lseek(std::uint64_t pos) {
+  auto res = ::lseek(get(), pos, SEEK_SET);
+  if (res < 0) {
+    throw std::system_error{errno, std::generic_category(), "lseek failed"};
+  }
+  return res;
+}
+
+std::int64_t file::read(std::span<std::byte> buf) {
+  auto res = ::read(fd_, buf.data(), buf.size_bytes());
+  if (res < 0) {
+    assert(0 < errno);
+    return -errno;
+  }
+  return res;
+}
+
+int file::read_exact(std::span<std::byte> buf) {
+  while (!buf.empty()) {
+    assert(buf.size_bytes() != 0);
+    auto res = read(buf);
+    if (res < 0) {
+      if (-res == EINTR || -res == EAGAIN) {
+        continue;
+      }
+      return res;
+    }
+    if (res == 0) {
+      fmt::println("EOF");
+      return -EINVAL;
+    }
+
+    buf = buf.subspan(res);
+  }
+  return 0;
+}
+
 std::int64_t file::read_at(std::uint64_t pos, std::span<std::byte> buf) {
   auto off = static_cast<off_t>(pos);
   if (off < 0)
     return -EINVAL;
   auto res = ::pread(fd_, buf.data(), buf.size_bytes(), off);
-  if (res < 0)
+  if (res < 0) {
+    assert(0 < errno);
     return -errno;
+  }
   return res;
 }
 
@@ -25,6 +70,7 @@ std::int64_t file::write_at(std::uint64_t pos, std::span<const std::byte> buf) {
 
 std::int64_t file::read_exact_at(std::uint64_t pos, std::span<std::byte> buf) {
   while (!buf.empty()) {
+    assert(buf.size_bytes() != 0);
     auto res = read_at(pos, buf);
     if (res < 0) {
       if (-res == EINTR || -res == EAGAIN) {
@@ -32,6 +78,7 @@ std::int64_t file::read_exact_at(std::uint64_t pos, std::span<std::byte> buf) {
       }
       return res;
     }
+    assert(res != 0);
 
     buf = buf.subspan(res);
     pos += res;
[…]

### 2024-06-08 src/sys/file.hpp

@@ -41,9 +41,17 @@ public:
     }
   }
 
+  std::uint64_t lseek(std::uint64_t pos);
+
   std::int64_t read_at(std::uint64_t pos, std::span<std::byte> buf);
 
+  std::int64_t read(std::span<std::byte> buf);
+  std::int64_t write(std::span<const std::byte> buf);
+
   std::int64_t write_at(std::uint64_t pos, std::span<const std::byte> buf);
+
+  int read_exact(std::span<std::byte> buf);
+  int write_all(std::span<const std::byte> buf);
 
   std::int64_t read_exact_at(std::uint64_t pos, std::span<std::byte> buf);
   std::int64_t write_all_at(std::uint64_t pos, std::span<const std::byte> buf);
@@ -53,4 +61,8 @@ private:
 };
 
 file open(const char *path, int mode, int prot);
+
+class child;
+
+file proc_mem(sys::child &child, int mode);
 } // namespace redstone::sys

### 2024-06-08 src/sys/ptrace.cpp

@@ -1,3 +1,5 @@
+#include <cassert>
+#include <cstdio>
 #include <sys/ptrace.h>
 #include <system_error>
 
@@ -8,8 +10,12 @@ namespace redstone::sys::ptrace {
 namespace {
 template <typename T, typename U>
 void ptrace_child(child &child, enum __ptrace_request req, T addr, U data) {
-  if (0 > ::ptrace(req, child.pid(), addr, data))
+  assert(child);
+
+  if (0 > ::ptrace(req, child.pid(), addr, data)) {
+    printf("command: %d\n", req);
     throw std::system_error{errno, std::generic_category(), "ptrace failed"};
+  }
 }
 } // namespace
 
@@ -17,7 +23,7 @@ void syscall(child &c) { ptrace_child(c, PTRACE_SYSCALL, 0, 0); }
 
 user_regs get_regs(child &c) {
   user_regs regs;
-  ptrace_child(c, PTRACE_GETREGS, 0, regs);
+  ptrace_child(c, PTRACE_GETREGS, 0, &regs);
   return regs;
 }
 

### 2024-06-08 paper/paper.tex
updated latex

@@
 Figure 1 provides a visual representation of the architecture powering Redstone.
+The box marked config represents the configuration settings of the entire simulator (particularly settings that dictate probabilities of event occurences during simulation such as packet dropping).
 The region marked "simulator space" represents the simulator process,
@@
 Within the simulator process there are multiple “machines”,
-representations of physical machines that, in production, would actually be different machines.
+representations of physical machines that, in production, would actually be different machines, and a root rng. The root rng represents the seed and alters program flow.
 Each of these machine abstractions have their own simulated disk space.
@@
 working with the machine’s “files” (the in-memory storage mocked up by the simulator).
+Additionally, the replicas effectively mock their own files, file descriptor tables, their own clock scales/jitter, and their own list of sockets.
 
@@
 {\fontsize{12}{15}\selectfont 
-The core of the simulated testing framework is its fault injection.
-By randomly (over the randomness of seed generation, rather than just randomly per-run)
-deciding whether a network will drop a packet,
-for example, the system is able to cover a breadth of ``environmental conditions",
-so to speak,
-that are harder to anticipate when designing the distributed system.
-
-Many of these ``environmental conditions"
-will inevitably cause failures in the distributed system due to insufficient edge case handling by the implementers of the system.
-This is a feature, not a bug.
+The core of the simulated testing framework is its randomness.
+By introducing randomness into whether or not a network packet is dropped or replayed, for example, the system is able to cover a breadth of inputs that are harder to anticipate when designing the distributed system.
+Many of these inputs will inevitably cause failures in the distributed system due to lack of cases covered by the distributed system itself.
 The whole purpose of distributed systems testing frameworks is to find these cases.
-
-The primary goal of Redstone, however,
-in addition to revealing these cases,
-is to make it simple to be able to deterministically find these “random” cases.
+The primary goal of Redstone though is, in addition to revealing these cases, make it simple to be able to deterministically find these “random” cases.
 The method by which Redstone seeks to do so is by introducing a seed.
-
-The seed is chosen by the user before the simulator runs.
-Wherever randomness is necessary
-% Then, rather whenever a random number is called in the simulation
-(say, to determine whether a packet should be dropped),
-the value can be pseudo-randomly generated based on the seed.
-
-Thus, the system performs a ``random" and yet totally deterministic program flow,
-which can be used in development for iteration on the tested system.
-When an interesting program flow is discovered by the user,
-instead of just relying on logs after the fact,
-the user can take note of the seed with which the simulation was run and simply run it again.
-
-Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two,
-the user can expect the exact same program flow to execute and to reproduce the same sequence of events as the one they see in their logs.
-Between these logs and the replicability of the program flow results,
-the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.
+The seed is chosen before the simulator runs by the user.
+Then, rather whenever a random number is called in the simulation (say, 0 if a packet should be dropped or 1 if a packet should be allowed through), the value can be derived from that seed using a pseudo random number generator.
+In our case, we use Xoshiro256**.
+Thus, the system covers a “random” program flow that can easily be iterated on.
+When an interesting program flow is discovered by the user, logs are played that cover what occurred during the run.
+However, instead of having to do the analysis entirely in post, the user can take note of the seed with which the simulation was run and simply run it again.
+Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two, the user can expect the exact same program flow to execute and to reproduce the same logs live.
+Between these logs and the replicability of the program flow results, the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.
 
@@
 
-\section{\txtrsdust Evaluation}
+\section{\txtrsdust Timed Performance}
 
@@
 
+\section{\txtrsdust Determinism Evaluation}
+
+{\fontsize{12}{15}\selectfont
+
+To ensure that Redstone is deterministic, we ran several tests with a simulated workload under several sets of fault parameters. In each test, we ran Redstone
+on with a single set of fault parameters (including seed) several times, comparing the output of each run to ensure that packet orderings and relative timings remained the same.
+Then, for that same set of fault parameters, we ran the simulator again but with a varying time scale and again compared, using ranges from 1 to 0.001 time scales.
+All outputs from a given seed + fault parameter list remained identical.
+Changes to the seed or the fault parameters likewise created a different output that was repeated across runs.
+
+The primary simulated workload was a server that received packets from a separate process, both running under Redstone.
+The server logged the time of arrival and the ordering of each packet number, and from those logs we are able to see that they are both identical across runs, and that faults are very visible when the probabilities rise.
+
+For example, in a workload where the drop chance was set to 40$\%$, we see many gaps in packet numbers arriving to the server, all in the same place by checking the diffs.
+
+}
+
 \section{\txtrsdust Conclusion}
@@
 {\fontsize{12}{15}\selectfont
-\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
-% Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.
-
-% // Talk about limitations, otherwise desired future plans/potential future work
 

### 2024-06-08 benches/fib.cpp
Initial simulator infrastructure and some basic hooks (#5)
* Begin rng work

* Add splitmix rng

* Add `xoshiro256**` rng

* Have `spdlog` use external `{fmt}`

* Many changes and cleanups, implement runners and some initial syscalls

* Implement UDP packet sequence

* Add file_descriptor type

* Refactor project layout

* Add dep on function_ref

* Make xoshiro256_star_star compatible with `<random>`

* Implement file descriptor wrapper type

* Overhaul runner API to allow reading and writing process memory

* Implement stdout_file_descriptor for testing

* Refactor hook api

* Implement init

@@ -1,0 +1,33 @@
+#include <chrono>
+#include <cstdint>
+#include <cstdio>
+#include <cstdlib>
+#include <iostream>
+#include <sys/socket.h>
+#include <unistd.h>
+
+int main() {
+
+  const auto start = std::chrono::steady_clock::now();
+
+  uint64_t a = 1;
+  uint64_t b = 1;
+
+  uint64_t iters = 5'000'000'000;
+
+  for (uint64_t i = 0; i < iters; ++i) {
+    uint64_t c = a + b;
+    a = b;
+    b = c;
+  }
+
+  const auto end = std::chrono::steady_clock::now();
+
+  std::cout << "took " << (end - start).count() << " to compute " << b
+            << std::endl;
+
+  //   for ()
+  return 0;
+}
+// 1121621100
+// 1157662211

### 2024-06-08 demo/echo.cpp

@@ -1,0 +1,43 @@
+#include <chrono>
+#include <cstdio>
+#include <cstring>
+#include <string>
+#include <sys/socket.h>
+#include <sys/un.h>
+#include <unistd.h>
+
+#include "demo.h"
+
+int main(int argc, char **argv) {
+  auto start = std::chrono::steady_clock::now();
+
+  int s = socket(AF_UNIX, SOCK_DGRAM, 0);
+  check_return_value(s);
+
+  auto addr = get_addr();
+  int rc = bind(s, reinterpret_cast<sockaddr *>(&addr), sizeof(addr));
+  check_return_value(rc);
+
+  std::string buf;
+
+  for (uint64_t i = 0; i < iters; ++i) {
+    auto t = std::chrono::steady_clock::now() - start;
+    auto t_s = std::chrono::duration_cast<std::chrono::seconds>(t);
+
+    buf.resize(8192);
+
+    struct sockaddr_storage storage;
+    socklen_t len;
+
+    auto ret =
+        recvfrom(s, buf.data(), buf.size(), 0, (sockaddr *)&storage, &len);
+    check_return_value(ret);
+    buf.resize(ret);
+
+    printf("received datagram: '%s'\n", buf.c_str());
+
+    if (buf == "done") {
+      break;
+    }
+  }
+}

### 2024-06-08 include/redstone/hook/hook.hpp

@@ -1,30 +1,0 @@
-#pragma once
-
-#include <cstdint>
-#include <map>
-#include <optional>
-#include <span>
-#include <string>
-#include <utility>
-#include <vector>
-
-namespace redstone::hook {
-struct handlers {
-  virtual std::optional<std::uint64_t>
-  maybe_handle(std::uint64_t sysno, std::span<const uint64_t, 6> args) {
-    return std::nullopt;
-  }
-
-  virtual void signaled(int signal) {}
-  virtual void exited(int status) {}
-  virtual void stopped(int signal) {}
-};
-
-struct command {
-  std::string path;
-  std::vector<std::string> args;
-  std::vector<std::pair<std::string, std::string>> env;
-};
-
-void run_command(const command &cmd, handlers &handlers);
-} // namespace redstone::hook

### 2024-06-08 src/hook/hook.cpp

@@ -1,182 +1,155 @@
-#include "redstone/hook/hook.hpp"
+#include "hook/hook.hpp"
 
+#include <mutex>
+#include <set>
+#include <string_view>
+#include <sys/auxv.h>
+#include <sys/prctl.h>
 #include <sys/ptrace.h>
+#include <sys/reg.h>
 #include <sys/syscall.h>
 #include <sys/types.h>
 #include <sys/user.h>
 #include <sys/wait.h>
 #include <unistd.h>
 
-#include <csignal>
+#include <algorithm>
 #include <cstdint>
-#include <cstdlib>
-#include <stdexcept>
-#include <system_error>
+#include <iterator>
+#include <span>
+#include <utility>
 #include <vector>
+
+#include <fmt/format.h>
+#include <fmt/ranges.h>
+#include <spdlog/spdlog.h>
+
+#include "hook/syscalls.hpp"
+#include "impls.hpp"
 
 namespace redstone::hook {
 namespace {
-struct ptrace_syscall_info {
-  uint8_t op;                   /* Type of system call stop */
-  uint32_t arch;                /* AUDIT_ARCH_* value; see seccomp(2) */
-  uint64_t instruction_pointer; /* CPU instruction pointer */
-  uint64_t stack_pointer;       /* CPU stack pointer */
-  union {
-    struct {            /* op == PTRACE_SYSCALL_INFO_ENTRY */
-      uint64_t nr;      /* System call number */
-      uint64_t args[6]; /* System call arguments */
-    } entry;
-    struct {            /* op == PTRACE_SYSCALL_INFO_EXIT */
-      int64_t rval;     /* System call return value */
-      uint8_t is_error; /* System call error flag;
-                        Boolean: does rval contain
-                        an error value (-ERRCODE) or
-                        a nonerror return value? */
-    } exit;
-    struct {             /* op == PTRACE_SYSCALL_INFO_SECCOMP */
-      uint64_t nr;       /* System call number */
-      uint64_t args[6];  /* System call arguments */
-      uint32_t ret_data; /* SECCOMP_RET_DATA portion
-                         of SECCOMP_RET_TRACE
-                         return value */
-    } seccomp;
+hook_result explicit_passthrough(sim::replica &, std::span<const uint64_t, 6>) {
[…]

### 2024-06-08 src/hook/hook.hpp

@@ -1,0 +1,85 @@
+#pragma once
+
+#include <cassert>
+#include <cstdint>
+#include <optional>
+#include <span>
+#include <string>
+#include <string_view>
+#include <vector>
+
+namespace redstone::sim {
+class replica;
+}
+
+namespace redstone {
+class simulator;
+class instance;
+} // namespace redstone
+
+namespace redstone::hook {
+enum class hook_kind {
+  explicit_passthrough,
+};
+
+enum class hook_result_kind {
+  handled,
+  passthrough,
+};
+
+struct passthrough_t {};
+inline constexpr passthrough_t passthrough;
+
+struct handled {
+  uint64_t result;
+
+  explicit handled(int64_t v) : result{static_cast<uint64_t>(v)} {}
+};
+
+struct error {
+  int cerrno;
+};
+
+struct hook_result {
+  hook_result_kind kind;
+  union {
+    std::uint64_t handled;
+  };
+
+  hook_result(passthrough_t) : kind{hook_result_kind::passthrough} {}
+  hook_result(struct handled h)
+      : kind{hook_result_kind::handled}, handled{h.result} {}
+  hook_result(error e)
+      : kind{hook_result_kind::handled},
+        handled{static_cast<uint64_t>(-e.cerrno)} {
+    assert(0 <= e.cerrno);
+  }
+};
+
+using hook = hook_result (*)(sim::replica &replica,
+                             std::span<const std::uint64_t, 6> args);
+
+std::span<const hook> hook_table();
+hook get_hook(uint64_t sys);
+
+struct handlers {
+  virtual std::optional<std::uint64_t>
+  maybe_handle(std::uint64_t sysno, std::span<const uint64_t, 6> args) {
+    return std::nullopt;
+  }
+
+  virtual void signaled(int signal) {}
+  virtual void exited(int status) {}
+  virtual void stopped(int signal) {}
+};
+
+struct command {
+  std::string path;
+  std::vector<std::string> args;
+  std::vector<std::string> env;
+};
+
+void run_command(const command &cmd, handlers &handlers);
+
+void print_stats();
+} // namespace redstone::hook

### 2024-06-08 src/hook/impls.cpp

@@ -1,0 +1,431 @@
+#include "impls.hpp"
+#include "hook.hpp"
+#include "metrics.hpp"
+#include "net/datagram_socket.hpp"
+#include "net/socket.hpp"
+#include "net/stream_socket.hpp"
+#include "sim/replica.hpp"
+
+#include <cassert>
+#include <cerrno>
+#include <chrono>
+#include <cstddef>
+#include <cstdint>
+#include <cstdio>
+#include <cstring>
+#include <ctime>
+#include <memory>
+#include <netinet/ip.h>
+#include <span>
+#include <spdlog/spdlog.h>
+#include <sys/socket.h>
+#include <sys/un.h>
+#include <system_error>
+#include <thread>
+#include <unistd.h>
+#include <vector>
+
+namespace redstone::hook {
+namespace {
+auto store_fragment_callback(sim::replica &replica, uintptr_t addr) {
+  return [&replica, addr](auto fragment) mutable {
+    auto &runner = replica.runner();
+    auto res = runner.read_memory(addr, fragment);
+    if (0 <= res) {
+      addr += res;
+    }
+    return res;
+  };
+}
+
+auto load_fragment_callback(sim::replica &replica, uintptr_t addr) {
+  return [&replica, addr](auto fragment) mutable {
+    auto &runner = replica.runner();
+    auto res = runner.write_memory(addr, fragment);
+    if (0 <= res) {
+      addr += res;
+    }
+    return res;
+  };
+}
+
+net::socket_addr parse_addr(sim::replica &replica, uintptr_t dest_addr,
+                            size_t dest_len, std::error_code &err) {
+  err = {};
+
+  struct sockaddr_storage addr_storage;
+
+  if (sizeof(addr_storage) < dest_len || dest_len < 2) {
+    err = std::error_code{EINVAL, std::generic_category()};
+    return {};
+  }
+
+  std::vector<std::byte> dest{dest_len, std::byte{}};
+  if (0 > replica.runner().read_memory(dest_addr, dest)) {
+    err = std::error_code{EFAULT, std::generic_category()};
+    return {};
+  }
+
+  memcpy(&addr_storage, dest.data(), dest.size());
+
+  net::address_family af;
+
+  switch (addr_storage.ss_family) {
+  case AF_INET: {
+    auto in_addr = reinterpret_cast<const sockaddr_in *>(&addr_storage);
+    net::ipv4_addr ip_addr{};
+
[…]

### 2024-06-08 src/hook/impls.hpp

@@ -1,0 +1,31 @@
+#pragma once
+
+#include "hook.hpp"
+#include <span>
+
+namespace redstone::hook {
+hook_result sys_write(sim::replica &replica,
+                      std::span<const std::uint64_t, 6> args);
+hook_result sys_read(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_close(sim::replica &replica,
+                      std::span<const std::uint64_t, 6> args);
+hook_result sys_open(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_socket(sim::replica &replica,
+                       std::span<const std::uint64_t, 6> args);
+hook_result sys_sendto(sim::replica &replica,
+                       std::span<const std::uint64_t, 6> args);
+hook_result sys_recvfrom(sim::replica &replica,
+                         std::span<const std::uint64_t, 6> args);
+hook_result sys_connect(sim::replica &replica,
+                        std::span<const std::uint64_t, 6> args);
+hook_result sys_read(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_bind(sim::replica &replica,
+                     std::span<const std::uint64_t, 6> args);
+hook_result sys_clock_gettime(sim::replica &replica,
+                              std::span<const std::uint64_t, 6> args);
+hook_result sys_clock_nanosleep(sim::replica &replica,
+                                std::span<const std::uint64_t, 6> args);
+} // namespace redstone::hook

### 2024-06-08 src/hook_impls.hpp

@@ -1,0 +1,30 @@
+#pragma once
+
+#include <cstdint>
+#include <span>
+
+#include "redstone.hpp"
+
+namespace redstone {
+enum class hook_kind {
+  explicit_passthrough,
+};
+
+enum class hook_result_kind {
+  handled,
+  passthrough,
+};
+
+struct hook_result {
+  hook_result_kind kind;
+  union {
+    std::uint64_t handled;
+  };
+};
+
+using hook = hook_result (*)(simulator &sim, instance &instance,
+                             std::span<const std::uint64_t, 6> args);
+
+std::span<const hook> hook_table();
+hook get_hook(uint64_t sys);
+} // namespace redstone

### 2024-06-08 src/main.cpp

@@ -1,78 +1,188 @@
-#include "redstone/hook/hook.hpp"
-#include "redstone/hook/syscalls.hpp"
-
-#include <bitset>
+#include <chrono>
+#include <csignal>
 #include <cstdio>
 #include <fmt/format.h>
-
+#include <map>
+#include <memory>
+#include <spdlog/spdlog.h>
+#include <stdexcept>
+#include <sys/random.h>
 #include <sys/syscall.h>
+#include <thread>
+#include <toml++/toml.hpp>
+#include <vector>
 
-namespace {
-constexpr int passthroughs[] = {
-    14,  // rt_sigprocmask
-    59,  // execve
-    12,  // brk
-    158, // arch_prctl
-    9,   // mmap
-    10,  // mprotect
-    11,  // munmap
-    39,  // getpid
-    231, // exit_group
-};
-std::bitset<500> get_passthroughs() {
-  std::bitset<500> all;
+#include "hook/hook.hpp"
+#include "metrics.hpp"
+#include "sim/machine.hpp"
+#include "sim/simulator.hpp"
 
-  for (int sysno : passthroughs) {
-    all.set(sysno);
-  }
-
-  return all;
+uint64_t random_seed() {
+  uint64_t buf;
+  getrandom(&buf, sizeof(buf), 0);
+  return buf;
 }
-} // namespace
 
-struct logging_handler : redstone::hook::handlers {
-  std::bitset<500> passthrough = get_passthroughs();
-
-  std::optional<std::uint64_t>
-  maybe_handle(std::uint64_t sysno,
-               std::span<const uint64_t, 6> args) override {
-    if (should_passthrough(sysno)) {
-      fmt::println("passthrough: {} ({})", sysno,
-                   redstone::hook::syscall_name(sysno));
-      return std::nullopt;
-    }
-
-    if (sysno == SYS_write && args[0] == 1) {
-      uintptr_t ptr = args[1];
-      size_t len = args[2];
-      fmt::println("write stdout ptr = {}, len = {}", (void *)ptr, len);
-      return len;
-    }
-
-    auto name = redstone::hook::syscall_name(sysno);
-    fmt::println("unhandled: {} ({})", sysno, name);
-    return std::nullopt;
-  }
-
-  void exited(int status) override { fmt::println("exited: {}", status); }
-
-private:
-  bool should_passthrough(std::uint64_t sysno) const {
-    if (passthrough.size() <= sysno) {
-      return true;
-    }
[…]

### 2024-06-08 src/metrics.cpp

@@ -1,0 +1,14 @@
+#include "metrics.hpp"
+
+#include <chrono>
+#include <fmt/chrono.h>
+#include <fmt/format.h>
+
+namespace redstone::metrics {
+void dump() {
+  fmt::println("metrics:");
+  fmt::println("sys_socket: average {}", sys_socket.average());
+  fmt::println("sys_close: average {}", sys_close.average());
+}
+
+} // namespace redstone::metrics

### 2024-06-08 src/net/fault.hpp

@@ -1,0 +1,38 @@
+#pragma once
+
+#include <chrono>
+#include <cstdio>
+#include <random>
+
+#include "random/rng.hpp"
+
+namespace redstone::net {
+struct net_fault_options {
+  std::chrono::nanoseconds min_latency{0};
+  std::chrono::nanoseconds max_latency{0};
+  double p_drop = 0.0;
+  double p_replay = 0.0;
+
+  template <typename Rng>
+  std::chrono::nanoseconds latency(Rng &&rng) const {
+    return random::gen_range(rng, min_latency,
+                             max_latency + std::chrono::nanoseconds{1});
+  }
+
+  template <typename Rng>
+  bool should_drop(Rng &&rng) const {
+    std::bernoulli_distribution dis{p_drop};
+    return dis(rng);
+  }
+
+  template <typename Rng>
+  std::size_t replay_count(Rng &&rng) const {
+    std::size_t n = 0;
+    for (;;) {
+      if (!random::gen_bool(rng, p_replay))
+        return n;
+      n++;
+    }
+  }
+};
+} // namespace redstone::net

### 2024-06-08 src/net/network.hpp

@@ -1,0 +1,23 @@
+#pragma once
+
+#include "socket.hpp"
+#include <memory>
+#include <mutex>
+#include <unordered_map>
+
+namespace redstone::net {
+class network {
+public:
+  network() = default;
+
+  std::error_code bind(socket_addr addr, std::shared_ptr<socket>);
+
+  void clear(const socket_addr &addr, socket *s);
+
+  std::shared_ptr<socket> get(const socket_addr &addr);
+
+private:
+  std::mutex mutex_;
+  std::unordered_map<socket_addr, std::weak_ptr<socket>> map_;
+};
+} // namespace redstone::net

### 2024-06-08 src/net/socket.cpp

@@ -1,0 +1,3 @@
+#include "socket.hpp"
+
+namespace redstone::net {} // namespace redstone::net

### 2024-06-08 src/net/stream_socket.cpp

@@ -1,0 +1,72 @@
+#include "stream_socket.hpp"
+#include "fault.hpp"
+#include "random/xoshiro.hpp"
+
+#include <algorithm>
+#include <cerrno>
+#include <cstddef>
+#include <vector>
+
+namespace redstone::net {
+std::int64_t stream_socket::recv(
+    tl::function_ref<int(std::span<const std::byte>)> write_data_callback,
+    std::size_t bytes) {
+  std::unique_lock lock{mutex_};
+
+  for (;;) {
+    if (buffer_.empty()) {
+      cond_.wait(lock);
+      continue;
+    }
+
+    const auto n = std::min(bytes, buffer_.size());
+
+    std::vector<std::byte> tmp;
+    tmp.reserve(n);
+    while (tmp.size() < n) {
+      tmp.push_back(buffer_.front());
+      buffer_.pop();
+    }
+
+    auto res = write_data_callback(tmp);
+    if (res < 0) {
+      return res;
+    }
+    return n;
+  }
+}
+
+std::int64_t stream_socket::send(
+    tl::function_ref<int(std::span<std::byte>)> read_data_callback,
+    std::size_t bytes) {
+  auto peer = peer_.lock();
+
+  std::unique_lock lock{peer->mutex_};
+
+  std::size_t sent = 0;
+
+  std::vector<std::byte> buf{bytes, std::byte{}};
+
+  auto res = read_data_callback(buf);
+  if (res < 0)
+    return res;
+
+  for (auto byte : buf)
+    peer->buffer_.push(byte);
+
+  peer->cond_.notify_all();
+
+  return res;
+}
+
+int stream_socket::connect(std::shared_ptr<stream_socket> other) {
+  if (listening_) {
+    return -EOPNOTSUPP;
+  }
+  if (get_af() != other->get_af()) {
+    return -EAFNOSUPPORT;
+  }
+  peer_ = other;
+  return 0;
+}
+} // namespace redstone::net

### 2024-06-08 src/net/stream_socket.hpp

@@ -1,0 +1,41 @@
+#pragma once
+
+#include "sim/file_descriptor.hpp"
+#include "socket.hpp"
+
+#include <condition_variable>
+#include <cstddef>
+#include <memory>
+#include <mutex>
+#include <queue>
+#include <span>
+#include <tl/function_ref.hpp>
+
+namespace redstone::net {
+class stream_socket : public socket {
+public:
+  explicit stream_socket(address_family af) : socket{af, socket_type::stream} {}
+
+  explicit stream_socket(address_family af, std::shared_ptr<stream_socket> peer)
+      : socket{af, socket_type::stream}, peer_{peer} {}
+
+  std::int64_t
+  recv(tl::function_ref<int(std::span<const std::byte>)> write_data_callback,
+       std::size_t bytes);
+
+  std::int64_t
+  send(tl::function_ref<int(std::span<std::byte>)> read_data_callback,
+       std::size_t bytes);
+
+  int connect(std::shared_ptr<stream_socket> other);
+
+  bool listening() const { return listening_; }
+
+private:
+  std::weak_ptr<stream_socket> peer_;
+  std::queue<std::byte> buffer_;
+  std::condition_variable cond_;
+  std::mutex mutex_;
+  bool listening_ = false;
+};
+} // namespace redstone::net

### 2024-06-08 src/net/udp.cpp

@@ -1,0 +1,133 @@
+// #include "net/udp.hpp"
+
+// #include <algorithm>
+// #include <chrono>
+// #include <cstddef>
+// #include <cstdint>
+// #include <limits>
+// #include <span>
+// #include <vector>
+
+// constexpr std::size_t max_udp_packet_size =
+//     std::numeric_limits<uint16_t>::max() - 128;
+
+// namespace redstone::net {
+// std::int64_t udp_stream::write(std::span<const std::byte> data) {
+//   if (max_udp_packet_size < data.size_bytes())
+//     data = data.subspan(0, max_udp_packet_size);
+
+//   if (fault_options_.should_drop(rng_))
+//     return data.size();
+
+//   const auto now = std::chrono::steady_clock::now();
+//   const auto latency = fault_options_.latency(rng_);
+//   const auto arrival = now + latency;
+
+//   udp_packet p{
+//       .arrival = arrival,
+//       .bytes = std::vector<std::byte>{data.begin(), data.end()},
+//   };
+
+//   std::vector<udp_packet> replays;
+//   const auto replay_count = fault_options_.replay_count(rng_);
+//   replays.reserve(replay_count);
+
+//   while (replays.size() < replay_count) {
+//     replays.push_back(p);
+//     replays.back().arrival = now + fault_options_.latency(rng_);
+//   }
+
+//   std::unique_lock lock{mutex_};
+
+//   packets_.push(std::move(p));
+//   for (auto &replay : replays) {
+//     packets_.push(std::move(replay));
+//   }
+
+//   cond_.notify_one();
+//   lock.unlock();
+
+//   for (auto &listener : select_write_)
+//     listener();
+
+//   return data.size_bytes();
+// }
+
+// std::int64_t udp_stream::read(std::span<std::byte> buf) {
+//   std::unique_lock lock{mutex_};
+
+//   while (!buf.empty()) {
+//     if (packets_.empty()) {
+//       cond_.wait(lock);
+//       continue;
+//     }
+
+//     auto &p = packets_.top();
+
+//     if (p.arrival > std::chrono::steady_clock::now()) {
+//       cond_.wait_until(lock, p.arrival);
+//       continue;
+//     }
+
+//     auto data = p.remaining();
+//     if (data.empty()) {
+//       packets_.pop();
+//       continue;
+//     }
+
+//     if (data.size_bytes() > buf.size_bytes())
+//       data = data.subspan(0, buf.size_bytes());
+
[…]

### 2024-06-08 src/net/udp.hpp

@@ -1,0 +1,73 @@
+// #pragma once
+
+// #include <chrono>
+// #include <condition_variable>
+// #include <cstddef>
+// #include <cstdint>
+// #include <functional>
+// #include <mutex>
+// #include <queue>
+// #include <span>
+// #include <vector>
+
+// #include "fault.hpp"
+// #include "random/xoshiro.hpp"
+
+// namespace redstone::net {
+// // A one-way UDP stream
+// class datagram_pipe {
+// public:
+//   void send(std::vector<std::byte> packet);
+//   std::vector<std::byte> recv();
+
+//   std::int64_t write(std::span<const std::byte> packet);
+//   std::int64_t read(std::span<std::byte> buf);
+
+// private:
+//   struct packet {
+//     std::chrono::steady_clock::time_point arrival;
+//     std::vector<std::byte> bytes;
+//     mutable std::size_t consumed = 0;
+
+//     friend bool operator<(const packet &lhs, const packet &rhs) {
+//       // Flip ordering
+//       return lhs.arrival > rhs.arrival;
+//     }
+
+//     friend bool operator>(const packet &lhs, const packet &rhs) {
+//       return rhs < lhs;
+//     }
+
+//     friend bool operator<=(const packet &lhs, const packet &rhs) {
+//       return !(rhs < lhs);
+//     }
+
+//     friend bool operator>=(const packet &lhs, const packet &rhs) {
+//       return !(lhs < rhs);
+//     }
+
+//     std::span<const std::byte> remaining() const {
+//       std::span<const std::byte> data = bytes;
+//       return data.subspan(consumed);
+//     }
+//   };
+
+//   std::mutex mutex_;
+//   std::condition_variable cond_;
+//   std::priority_queue<packet> packets_;
+
+//   std::vector<std::function<void()>> select_read_;
+//   std::vector<std::function<void()>> select_write_;
+
+//   const net_fault_options fault_options_;
+//   // const std::chrono::nanoseconds min_latency_{1000};
+//   // const std::chrono::nanoseconds max_latency_{1001};
+//   // const double drop_chance_ = 0.01;
+
+//   // Only accessed by writer
+//   random::xoshiro256_star_star rng_;
+
+//   void send_packet(std::span<const std::byte> packet);
+//   packet recv_packet();
+// };
+// } // namespace redstone::net

### 2024-06-08 src/random/getrandom.hpp

@@ -1,0 +1,9 @@
+#pragma once
+
+#include <cstddef>
+#include <cstdint>
+#include <span>
+
+#include <sys/random.h>
+
+namespace redstone::random {} // namespace redstone::random

### 2024-06-08 src/random/rng.hpp

@@ -1,0 +1,81 @@
+#pragma once
+
+#include <cassert>
+#include <chrono>
+#include <cstddef>
+#include <cstdint>
+#include <limits>
+
+namespace redstone::random {
+template <typename Rng>
+struct rng_traits {
+  static constexpr size_t seed_size = Rng::seed_size;
+};
+
+template <typename Rng, typename Source>
+Rng seed_from_rng(Source &source) {
+  std::byte seed[rng_traits<Rng>::seed_size];
+  source.fill_bytes(seed);
+  return Rng{seed};
+}
+
+template <typename T>
+struct sample_uniform {
+  template <typename Rng>
+  T operator()(Rng &&, const T &first, const T &last) = delete;
+};
+
+template <>
+struct sample_uniform<uint64_t> {
+  uint64_t first;
+  uint64_t last;
+
+  template <typename Rng>
+  uint64_t operator()(Rng &&rng, uint64_t first, uint64_t last) {
+    auto width = last - first;
+    auto v = rng.next();
+    return first + (v % width);
+  }
+};
+
+template <>
+struct sample_uniform<long> {
+  long first;
+  long last;
+
+  template <typename Rng>
+  long operator()(Rng &&rng, long first, long last) {
+    return sample_uniform<uint64_t>{}(rng, first, last);
+  }
+};
+
+template <typename Repr, typename Period>
+struct sample_uniform<std::chrono::duration<Repr, Period>> {
+
+  template <typename Rng>
+  std::chrono::duration<Repr, Period>
+  operator()(Rng &&rng, std::chrono::duration<Repr, Period> first,
+             std::chrono::duration<Repr, Period> last) {
+    auto v = sample_uniform<Repr>{}(rng, first.count(), last.count());
+    return std::chrono::duration<Repr, Period>{v};
+  }
+};
+
+template <typename T, typename Rng>
+T gen_range(Rng &&rng, T first, T last) {
+  return sample_uniform<T>{}(rng, first, last);
+}
+
+template <typename Rng>
+bool gen_bool(Rng &&rng, double p) {
+  assert(0.0 <= p && p <= 1.0);
+
+  auto threshold = static_cast<uint64_t>(p * (2.0 * uint64_t(1llu << 63)));
+  auto v = rng.next();
+
+  if (threshold == std::numeric_limits<uint64_t>::max())
+    return true;
+
+  return v < threshold;
+}
+} // namespace redstone::random

### 2024-06-08 src/random/xoshiro.hpp

@@ -1,0 +1,90 @@
+#pragma once
+
+#include <bit>
+#include <cstddef>
+#include <cstdint>
+#include <cstring>
+#include <span>
+#include <type_traits>
+#include <utility>
+
+namespace redstone::random {
+class xoshiro256_star_star {
+public:
+  using result_type = uint64_t;
+
+  static constexpr size_t seed_size = 32;
+
+  xoshiro256_star_star() : state_{} {}
+
+  template <typename SeedSeq>
+  explicit xoshiro256_star_star(SeedSeq &seq) {
+    seed(seq);
+  }
+
+  explicit xoshiro256_star_star(std::span<const std::byte, seed_size> seed) {
+    std::memcpy(state_, seed.data(), seed.size_bytes());
+  }
+
+  uint64_t operator()() { return next(); }
+
+  template <typename SeedSeq>
+  void seed(SeedSeq &seq) {
+    uint32_t seed[8];
+    seq.generate(seed, seed + 8);
+    std::memcpy(state_, seed, sizeof(seed));
+  }
+
+  static constexpr uint64_t min() { return 0; }
+  static constexpr uint64_t max() { return UINT64_MAX; }
+
+  uint64_t next() {
+    const uint64_t result = std::rotl(state_[1] * 5, 7) * 9;
+
+    const uint64_t t = state_[1] << 17;
+
+    state_[2] ^= state_[0];
+    state_[3] ^= state_[1];
+    state_[1] ^= state_[2];
+    state_[0] ^= state_[3];
+
+    state_[2] ^= t;
+
+    state_[3] = std::rotl(state_[3], 45);
+
+    return result;
+  }
+
+  void fill_bytes(std::span<std::byte> buf) {
+    while (8 <= buf.size_bytes()) {
+      uint64_t block = next();
+      std::memcpy(buf.data(), &block, sizeof(block));
+      buf = buf.subspan(8);
+    }
+
+    uint64_t block = next();
+    std::memcpy(buf.data(), &block, buf.size_bytes());
+  }
+
+  void set_seed(uint64_t a, uint64_t b, uint64_t c, uint64_t d) {
+    state_[0] = a;
+    state_[1] = b;
+    state_[2] = c;
+    state_[3] = d;
+  }
+
+  template <typename Rng>
+  void seed_from(Rng &rng) {
+    static_assert(
+        std::is_same_v<decltype(std::declval<Rng &>().next()), uint64_t>);
+
[…]

### 2024-06-08 src/sim/file_descriptor.cpp

@@ -1,0 +1,108 @@
+#include "sim/file_descriptor.hpp"
+#include "sys/file.hpp"
+
+#include <cassert>
+#include <cstddef>
+#include <memory>
+#include <spdlog/spdlog.h>
+#include <string_view>
+#include <vector>
+
+namespace redstone::sim {
+std::shared_ptr<file_descriptor> file_descriptor_table::get(int fd) {
+  std::unique_lock lock{mutex_};
+  return table_[fd];
+}
+
+int file_descriptor_table::close(int fd) {
+  std::unique_lock lock{mutex_};
+  auto it = table_.find(fd);
+  if (it == table_.end() || !it->second) {
+    return -EBADFD;
+  }
+
+  assert(is_simulated(fd));
+  assert(0 <= fd);
+
+  table_.erase(it);
+  unused_.push_back(fd);
+  return 0;
+}
+
+int file_descriptor_table::insert(std::shared_ptr<file_descriptor> fildes) {
+  std::unique_lock lock{mutex_};
+
+  int fd = -1;
+
+  if (!unused_.empty()) {
+    fd = unused_.back();
+    unused_.pop_back();
+  } else {
+    if (capacity <= table_.size()) {
+      return -1;
+    }
+
+    fd = static_cast<int>(table_.size());
+
+    // Simulated bit already set, this should not be a valid fd
+    assert(!is_simulated(fd));
+    fd |= simulated;
+  }
+
+  assert(0 <= fd);
+  assert(is_simulated(fd));
+
+  auto &slot = table_[fd];
+  assert(!slot);
+  slot = std::move(fildes);
+  return fd;
+}
+
+namespace {
+class stdout_file_descriptor final : public file_descriptor {
+public:
+  stdout_file_descriptor() = default;
+
+  std::int64_t write(tl::function_ref<int(std::span<std::byte>)> load,
+                     const std::size_t bytes) final {
+    std::vector buf{8192, std::byte{}};
+
+    std::size_t done = 0;
+
+    fmt::println("output: '{}'", std::string_view{(const char *)buf.data(), 4});
+
+    while (done < bytes) {
+      std::span tmp = buf;
+
+      if (tmp.size_bytes() > bytes) {
+        tmp = tmp.subspan(0, bytes);
+      }
+
+      auto res = load(tmp);
+      if (res < 0) {
+        return res;
+      }
+
+      fmt::println("output: '{}'",
[…]

### 2024-06-08 src/sim/file_descriptor.hpp

@@ -1,0 +1,53 @@
+#pragma once
+
+#include <cerrno>
+#include <cstddef>
+#include <memory>
+#include <mutex>
+#include <span>
+#include <tl/function_ref.hpp>
+#include <unordered_map>
+#include <vector>
+
+namespace redstone::sim {
+class file_descriptor {
+public:
+  virtual ~file_descriptor() = default;
+
+  virtual std::int64_t
+  read(tl::function_ref<int(std::span<const std::byte>)> store,
+       std::size_t bytes) {
+    return -EINVAL;
+  }
+
+  virtual std::int64_t write(tl::function_ref<int(std::span<std::byte>)> load,
+                             std::size_t bytes) {
+    return -EINVAL;
+  };
+
+private:
+};
+
+class file_descriptor_table {
+public:
+  file_descriptor_table() = default;
+
+  static bool is_simulated(int fd) { return (fd & simulated) != 0; }
+
+  std::shared_ptr<file_descriptor> get(int fd);
+  int close(int fd);
+  int insert(std::shared_ptr<file_descriptor> fildes);
+
+private:
+  static constexpr int simulated = 1 << 30;
+  static constexpr int capacity = (1u << 30) - 1;
+
+  int counter_ = 1 << 30;
+
+  std::mutex mutex_;
+  std::unordered_map<int, std::shared_ptr<file_descriptor>> table_;
+  std::vector<int> unused_;
+};
+
+std::shared_ptr<file_descriptor> stdout_fd();
+} // namespace redstone::sim

### 2024-06-08 src/sim/machine.cpp

@@ -1,0 +1,9 @@
+#include "machine.hpp"
+
+namespace redstone::sim {
+void machine::start() {
+  runner_options_.machine = this;
+  auto handle = runner_(runner_options_);
+  current_ = std::make_shared<replica>(handle, *this);
+}
+} // namespace redstone::sim

### 2024-06-08 src/sim/machine.hpp

@@ -1,0 +1,32 @@
+#pragma once
+
+#include <functional>
+#include <memory>
+
+#include "replica.hpp"
+#include "runner.hpp"
+#include "simulator.hpp"
+
+namespace redstone::sim {
+class simulator;
+
+class machine {
+public:
+  explicit machine(simulator &sim, runner_options options)
+      : sim_{&sim}, runner_options_{std::move(options)} {}
+
+  std::shared_ptr<replica> current_replica() { return current_; }
+
+  void start();
+
+  sim::simulator &sim() { return *sim_; }
+
+private:
+  runner_options runner_options_;
+  std::shared_ptr<replica> current_;
+  std::function<std::shared_ptr<runner_handle>(const runner_options &)> runner_{
+      ptrace_run};
+  sim::simulator *sim_;
+  net::network *net_;
+};
+} // namespace redstone::sim

### 2024-06-08 src/sim/replica.cpp

@@ -1,0 +1,15 @@
+#include "replica.hpp"
+#include "machine.hpp"
+#include "simulator.hpp"
+#include <memory>
+
+namespace redstone::sim {
+replica::~replica() = default;
+
+replica::replica(std::shared_ptr<runner_handle> handle, machine &m)
+    : handle_{std::move(handle)}, machine_{&m} {}
+
+net::network &replica::network() { return machine_->sim().net(); }
+
+simulator &replica::sim() { return machine_->sim(); }
+} // namespace redstone::sim

### 2024-06-08 src/sim/replica.hpp

@@ -1,0 +1,42 @@
+#pragma once
+
+#include "file_descriptor.hpp"
+#include "net/network.hpp"
+#include "runner.hpp"
+
+#include <cassert>
+#include <chrono>
+#include <memory>
+
+namespace redstone::sim {
+using clock = std::chrono::steady_clock;
+
+class simulator;
+
+class replica {
+public:
+  ~replica();
+
+  explicit replica(std::shared_ptr<runner_handle> handle, machine &m);
+
+  file_descriptor_table &fd_table() { return fd_table_; }
+
+  runner_handle &runner() {
+    assert(handle_);
+    return *handle_;
+  }
+
+  net::network &network();
+
+  simulator &sim();
+
+  clock::time_point epoch() const { return epoch_; }
+
+private:
+  std::shared_ptr<runner_handle> handle_;
+  machine *machine_ = nullptr;
+  net::network *net_;
+  file_descriptor_table fd_table_;
+  const clock::time_point epoch_ = clock::now();
+};
+} // namespace redstone::sim

### 2024-06-08 src/sim/runner.hpp

@@ -1,0 +1,44 @@
+#pragma once
+
+#include <csignal>
+#include <memory>
+#include <optional>
+#include <span>
+#include <string>
+#include <variant>
+#include <vector>
+
+#include "sys/child.hpp"
+
+namespace redstone {
+class simulator;
+class instance;
+} // namespace redstone
+
+namespace redstone::sim {
+class machine;
+
+struct runner_options {
+  std::string path;
+  std::vector<std::string> args;
+  std::vector<std::string> env;
+  machine *machine;
+};
+
+struct runner_result {
+  std::variant<sys::child::exited, sys::child::terminated> status;
+};
+
+/// Communicate with an active runner
+struct runner_handle {
+  virtual ~runner_handle() = default;
+
+  virtual void kill(int signal = SIGTERM) = 0;
+  virtual void wait() = 0;
+  virtual std::optional<sys::child::run_state> state() = 0;
+  virtual int write_memory(uintptr_t ptr, std::span<const std::byte> data) = 0;
+  virtual int read_memory(uintptr_t ptr, std::span<std::byte> data) = 0;
+};
+
+std::shared_ptr<runner_handle> ptrace_run(const runner_options &options);
+} // namespace redstone::sim

### 2024-06-08 src/sim/runner/ptrace.cpp

@@ -1,0 +1,397 @@
+#include "sim/runner.hpp"
+
+#include <cassert>
+#include <cerrno>
+#include <chrono>
+#include <condition_variable>
+#include <csignal>
+#include <cstddef>
+#include <cstdint>
+#include <cstdio>
+#include <cstring>
+#include <fcntl.h>
+#include <iostream>
+#include <memory>
+#include <mutex>
+#include <optional>
+#include <span>
+#include <stdexcept>
+#include <sys/auxv.h>
+#include <sys/prctl.h>
+#include <sys/ptrace.h>
+#include <sys/reg.h>
+#include <sys/syscall.h>
+#include <sys/types.h>
+#include <sys/user.h>
+#include <sys/wait.h>
+#include <system_error>
+#include <thread>
+#include <unistd.h>
+#include <variant>
+#include <vector>
+
+#include <spdlog/spdlog.h>
+
+#include "hook/hook.hpp"
+#include "hook/syscalls.hpp"
+#include "sim/machine.hpp"
+#include "sim/replica.hpp"
+#include "sys/child.hpp"
+#include "sys/file.hpp"
+#include "sys/ptrace.hpp"
+
+namespace redstone::sim {
+
+class barrier {
+public:
+  explicit barrier(std::size_t count) : count_{count} {}
+
+  void wait() {
+    std::unique_lock lock{mutex_};
+    assert(current_ != 0);
+
+    current_--;
+
+    if (current_ == 0) {
+      current_ = count_;
+      epoch_++;
+      cond_.notify_all();
+      return;
+    }
+
+    auto epoch = epoch_;
+
+    while (epoch == epoch_) {
+      cond_.wait(lock);
+    }
+  }
+
+private:
+  std::size_t count_;
+  std::size_t current_ = count_;
+  std::size_t epoch_ = 0;
+  std::mutex mutex_;
+  std::condition_variable cond_;
+};
+namespace {
+sys::child spawn(const runner_options &options) {
+  if (options.args.at(0) != options.path) {
+    throw std::invalid_argument{
+        "spawn: argv[0] must be the same as the provided path"};
+  }
+
+  std::vector<char *> argv;
+
+  for (auto &arg : options.args) {
+    argv.push_back(const_cast<char *>(arg.c_str()));
+  }
+  argv.push_back(nullptr);
+
+  std::vector<char *> env;
+
+  for (auto &var : options.env) {
[…]

### 2024-06-08 src/sim/simulator.hpp

@@ -1,0 +1,39 @@
+#pragma once
+
+#include <array>
+#include <cstdint>
+#include <utility>
+#include <vector>
+
+#include "machine.hpp"
+#include "net/fault.hpp"
+#include "random/splitmix.hpp"
+#include "random/xoshiro.hpp"
+
+namespace redstone::sim {
+struct options {
+  net::net_fault_options net_faults{};
+  double time_scale = 1.0;
+  std::uint64_t seed;
+};
+
+class simulator {
+public:
+  explicit simulator(options &&o) : options_{std::move(o)} {
+    random::split_mix seed_source{options_.seed};
+    rng_.seed_from(seed_source);
+  }
+
+  net::network &net() { return net_; }
+
+  random::xoshiro256_star_star &rng() { return rng_; }
+
+  const options &initial_options() const { return options_; }
+
+private:
+  random::xoshiro256_star_star rng_;
+  std::vector<machine> machines_;
+  net::network net_;
+  options options_;
+};
+} // namespace redstone::sim

### 2024-06-08 src/simple.cpp

@@ -1,7 +1,22 @@
+#include <cassert>
+#include <cstdio>
+#include <ctime>
 #include <sqlite3.h>
 #include <stdexcept>
+#include <sys/socket.h>
+#include <unistd.h>
 
 int main() {
+  int s = socket(AF_INET, SOCK_DGRAM, 0);
+  assert(s > 0);
+  ::close(s);
+
+  printf("hi!\n");
+  return 0;
+
+  struct timespec tm;
+  clock_gettime(CLOCK_BOOTTIME, &tm);
+
   sqlite3 *db;
   int rc = sqlite3_open("sqlite.db", &db);
   if (rc < 0) {

### 2024-06-08 src/sys/child.cpp

@@ -1,0 +1,47 @@
+#include "child.hpp"
+
+#include <cstdio>
+#include <sys/wait.h>
+
+#include <stdexcept>
+#include <system_error>
+
+namespace redstone::sys {
+int child::wait() {
+  state_ = std::nullopt;
+
+  int status;
+  int rc = waitpid(pid(), &status, 0);
+
+  if (rc < 0) {
+    throw std::system_error{errno, std::generic_category(), "waitpid failed"};
+  }
+
+  if (WIFCONTINUED(status)) {
+    state_ = running{};
+  } else if (WIFSTOPPED(status)) {
+    state_ = stopped{.signal = WSTOPSIG(status)};
+  } else if (WIFEXITED(status)) {
+    state_ = exited{WEXITSTATUS(status)};
+    pid_ = -1;
+  } else if (WIFSIGNALED(status)) {
+    state_ = terminated{WTERMSIG(status)};
+    pid_ = -1;
+  } else {
+    throw std::runtime_error{"unknown waitpid status"};
+  }
+
+  return status;
+}
+
+void child::terminate(int signal) {
+  if (!*this) {
+    throw std::invalid_argument{"terminate of not running process"};
+  }
+
+  int rc = ::kill(pid(), signal);
+  if (rc < 0) {
+    throw std::system_error{errno, std::generic_category(), "kill failed"};
+  }
+}
+} // namespace redstone::sys

### 2024-06-08 src/sys/command.cpp

@@ -1,0 +1,5 @@
+#include "command.hpp"
+
+namespace redstone::sys {
+child command::spawn() {}
+} // namespace redstone::sys

### 2024-06-08 src/sys/command.hpp

@@ -1,0 +1,17 @@
+#pragma once
+
+#include "sys/child.hpp"
+
+#include <string>
+#include <utility>
+#include <vector>
+
+namespace redstone::sys {
+struct command {
+  std::string path;
+  std::vector<std::string> args;
+  std::vector<std::pair<std::string, std::string>> env;
+
+  [[nodiscard]] child spawn();
+};
+} // namespace redstone::sys

### 2024-06-08 src/sys/file.cpp

@@ -1,0 +1,117 @@
+#include "file.hpp"
+#include "child.hpp"
+#include <cassert>
+#include <cerrno>
+#include <cstdio>
+#include <fcntl.h>
+#include <fmt/core.h>
+#include <system_error>
+#include <unistd.h>
+
+namespace redstone::sys {
+std::uint64_t file::lseek(std::uint64_t pos) {
+  auto res = ::lseek(get(), pos, SEEK_SET);
+  if (res < 0) {
+    throw std::system_error{errno, std::generic_category(), "lseek failed"};
+  }
+  return res;
+}
+
+std::int64_t file::read(std::span<std::byte> buf) {
+  auto res = ::read(fd_, buf.data(), buf.size_bytes());
+  if (res < 0) {
+    assert(0 < errno);
+    return -errno;
+  }
+  return res;
+}
+
+int file::read_exact(std::span<std::byte> buf) {
+  while (!buf.empty()) {
+    assert(buf.size_bytes() != 0);
+    auto res = read(buf);
+    if (res < 0) {
+      if (-res == EINTR || -res == EAGAIN) {
+        continue;
+      }
+      return res;
+    }
+    if (res == 0) {
+      fmt::println("EOF");
+      return -EINVAL;
+    }
+
+    buf = buf.subspan(res);
+  }
+  return 0;
+}
+
+std::int64_t file::read_at(std::uint64_t pos, std::span<std::byte> buf) {
+  auto off = static_cast<off_t>(pos);
+  if (off < 0)
+    return -EINVAL;
+  auto res = ::pread(fd_, buf.data(), buf.size_bytes(), off);
+  if (res < 0) {
+    assert(0 < errno);
+    return -errno;
+  }
+  return res;
+}
+
+std::int64_t file::write_at(std::uint64_t pos, std::span<const std::byte> buf) {
+  auto off = static_cast<off_t>(pos);
+  if (off < 0)
+    return -EINVAL;
+  auto res = ::pwrite(fd_, buf.data(), buf.size_bytes(), off);
+  if (res < 0)
+    return -errno;
+  return res;
+}
+
+std::int64_t file::read_exact_at(std::uint64_t pos, std::span<std::byte> buf) {
+  while (!buf.empty()) {
+    assert(buf.size_bytes() != 0);
+    auto res = read_at(pos, buf);
+    if (res < 0) {
+      if (-res == EINTR || -res == EAGAIN) {
+        continue;
+      }
+      return res;
+    }
+    assert(res != 0);
+
[…]

### 2024-06-08 src/sys/file.hpp

@@ -1,0 +1,68 @@
+#pragma once
+
+#include <cstdint>
+#include <span>
+#include <unistd.h>
+#include <utility>
+
+namespace redstone::sys {
+class file {
+public:
+  ~file() { reset(); }
+
+  file() = default;
+
+  explicit file(int fd) : fd_{fd} {}
+
+  file(file &&f) : fd_{f.release()} {}
+
+  file(const file &) = delete;
+
+  file &operator=(file &&f) {
+    std::swap(fd_, f.fd_);
+    return *this;
+  }
+
+  file &operator=(const file &f) = delete;
+
+  explicit operator bool() const { return 0 <= fd_; }
+
+  int get() const { return fd_; }
+
+  int release() {
+    auto fd = fd_;
+    fd_ = -1;
+    return fd;
+  }
+
+  void reset() {
+    if (*this) {
+      ::close(release());
+    }
+  }
+
+  std::uint64_t lseek(std::uint64_t pos);
+
+  std::int64_t read_at(std::uint64_t pos, std::span<std::byte> buf);
+
+  std::int64_t read(std::span<std::byte> buf);
+  std::int64_t write(std::span<const std::byte> buf);
+
+  std::int64_t write_at(std::uint64_t pos, std::span<const std::byte> buf);
+
+  int read_exact(std::span<std::byte> buf);
+  int write_all(std::span<const std::byte> buf);
+
+  std::int64_t read_exact_at(std::uint64_t pos, std::span<std::byte> buf);
+  std::int64_t write_all_at(std::uint64_t pos, std::span<const std::byte> buf);
+
+private:
+  int fd_ = -1;
+};
+
+file open(const char *path, int mode, int prot);
+
+class child;
+
+file proc_mem(sys::child &child, int mode);
+} // namespace redstone::sys

### 2024-06-08 src/sys/ptrace.cpp

@@ -1,0 +1,41 @@
+#include <cassert>
+#include <cstdio>
+#include <sys/ptrace.h>
+#include <system_error>
+
+#include "child.hpp"
+#include "ptrace.hpp"
+
+namespace redstone::sys::ptrace {
+namespace {
+template <typename T, typename U>
+void ptrace_child(child &child, enum __ptrace_request req, T addr, U data) {
+  assert(child);
+
+  if (0 > ::ptrace(req, child.pid(), addr, data)) {
+    printf("command: %d\n", req);
+    throw std::system_error{errno, std::generic_category(), "ptrace failed"};
+  }
+}
+} // namespace
+
+void syscall(child &c) { ptrace_child(c, PTRACE_SYSCALL, 0, 0); }
+
+user_regs get_regs(child &c) {
+  user_regs regs;
+  ptrace_child(c, PTRACE_GETREGS, 0, &regs);
+  return regs;
+}
+
+void set_regs(child &c, const user_regs &regs) {
+  ptrace_child(c, PTRACE_SETREGS, 0, &regs);
+}
+
+void set_options(child &c, int options) {
+  ptrace_child(c, PTRACE_SETOPTIONS, 0, options);
+}
+
+void get_syscall_info(child &c, syscall_info *info) {
+  ptrace_child(c, PTRACE_GET_SYSCALL_INFO, sizeof(*info), info);
+}
+} // namespace redstone::sys::ptrace

### 2024-06-08 paper/paper.tex
Minor fixes; final submission already done

@@
 \linespread{1.25}
-
-%-------------------------------------------------------------------------------
-\begin{filecontents}{\jobname.bib}
-%-------------------------------------------------------------------------------
-@Book{arpachiDusseau18:osbook,
-author =       {Arpaci-Dusseau, Remzi H. and Arpaci-Dusseau Andrea C.},
-title =        {Operating Systems: Three Easy Pieces},
-publisher =    {Arpaci-Dusseau Books, LLC},
-year =         2015,
-edition =      {1.00},
-note =         {\url{http://pages.cs.wisc.edu/~remzi/OSTEP/}}
-}
-@InProceedings{waldspurger02,
-author =       {Waldspurger, Carl A.},
-title =        {Memory resource management in {VMware ESX} server},
-booktitle =    {USENIX Symposium on Operating System Design and
-Implementation (OSDI)},
-year =         2002,
-pages =        {181--194},
-note =         {\url{https://www.usenix.org/legacy/event/osdi02/tech/waldspurger/waldspurger.pdf}}}
-\end{filecontents}
 
@@
 Although their work is not a research paper,
-the TigerBeetle team has provided inspiration to Redstone in their work developing a testing system for their database.
+the TigerBeetle \cite{tigerbeetle} team has provided inspiration to Redstone in their work developing a testing system for their database.
 This work heavily involved hastened testing of simulated distributed system faults.
@@
 Within the simulator process there are multiple “machines”,
-representations of physical machines that, in production, would actually be different machines, and a root rng. The root rng represents the seed and alters program flow.
+representations of physical machines that, in production, would actually be different machines, and a root RNG. The root RNG represents the seed and alters program flow.
 Each of these machine abstractions have their own simulated disk space.
@@
 {\fontsize{12}{15}\selectfont 
+Redstone introduces a deterministic simulation testing framework for distributed systems,
+intercepting system calls and injecting faults in all necessary subsystems,
+including network, disk, and clocks, dependent on a seed.
+We show that,
+although we depend on a comparatively-slow \texttt{ptrace}-based design that introduces significant overhead,
+we are able to both introduce faults and deterministically replicate failure conditions.
+
+}
+
+\section{\txtrsdust Works Consulted}
+
+{\fontsize{12}{15}\selectfont 
+\begin{itemize}
+\item https://tigerbeetle.com/blog
+\item https://jepsen.io/analyses
+\item https://man7.org/linux/man-pages/man2/ptrace.2.html
+\item https://www.man7.org/linux/man-pages/man8/ld.so.8.html
+\item https://man7.org/linux/man-pages/man7/vdso.7.html
+\end{itemize}
 
@@
 %-------------------------------------------------------------------------------
-\bibliographystyle{plain}
-\bibliography{\jobname}
+% \bibliographystyle{plain}
+% \bibliography{\jobname}
 
@@
 \end{document}
+
+\end{thebibliography}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2024-06-08 determinism.py
Fix determinism check script

@@ -1,19 +1,31 @@
 import subprocess
 import hashlib
+import time
 
 RUNS = 100
-args = ["./build/redstone", "sim.toml"]
+args = ["./build/redstone", "demo_repro3.toml"]
 
 sha = None
 
-for _ in range(RUNS):
+runs = []
+
+
+
+for i in range(RUNS):
     result = subprocess.run(args, stdout=subprocess.PIPE)
     result.check_returncode()
 
     print("finished run!")
 
-    iter_sha = hashlib.sha256(result.stdout)
+    runs.append(result.stdout)
+
+    with open(f"runs/run{i}.txt", "wb") as f:
+        _ = f.write(result.stdout)
+
+    iter_sha = hashlib.sha256(result.stdout).digest()
     if sha is None:
         sha = iter_sha
     if sha != iter_sha:
+        print(sha, iter_sha)
         print("run had different sha")
+    time.sleep(1)
